### 2018-01-01 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

\documentclass[]{llncs}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments

% lncs 
\usepackage{makeidx}
\institute{FH Dortmund, \\ \texttt{}}

\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Daniel Paredes},
            pdftitle={The power of dark silicon},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

\title{The power of dark silicon}
\author{Daniel Paredes}
\date{}

\begin{document}
\maketitle
\begin{abstract}
Sit amet mauris. Curabitur a quam. Aliquam neque. Nam nunc nunc, lacinia
sed, varius quis, iaculis eget, ante. Nulla dictum justo eu lacus.
Phasellus sit amet quam. Nullam sodales. Cras non magna eu est
consectetuer faucibus. Donec tempor lobortis turpis. Sed tellus velit,
ullamcorper ac, fringilla vitae, sodales nec, purus. Morbi aliquet risus
in mi.

% lncs keyword extension 
\keywords{hope, luke, ewoks}

\end{abstract}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

I need an introduction\ldots{}

\hypertarget{using-argumentation-to-explain-ambiguity-in-requirements-elicitation-interviews}{%
\section{Using Argumentation to Explain Ambiguity in Requirements
Elicitation
Interviews}\label{using-argumentation-to-explain-ambiguity-in-requirements-elicitation-interviews}}

One of the major causes of ambiguities in elicitation interviews is the
prescense of tacit knowlegde. In some cases ambiguities can't be always
be explained as separated term, sometimes it is required to have a
context. Even under these circunstances, the analyst must be able to
identify and alleviate them in order to elicitate relevant information
of the system. For this purpose it is necessary to provide the analyst
with proper tools. In this paper Yehia Elrakaiby et al. {[}1{]} proposed
a theorical framework to overcome ambiguity during interviews in the
elicitation phase. The framework is based on the ``Argumentation
theory''.

In that sense, Elrakaiby et al.~focus on one type of ambiguities, the
``acceptance unclarity''. An acceptance unclarity occurs everytime the
analyst is able to assign an interpretation or meaning to the speech
fragment of the stakeholder, the interpretation matches the intended
meaning of the stakeholder, but the interpretation is not acceptable or
justified. It could be either because it seems to be inaccurate to
comprehend the problem, or analysts identify inconsistencies with their
current understanding of the problem or domain knowlegde. By using
argumentation theory framework, statements and ambiguities can be
characterized as ``arguments'' and ``attacks'' respectevely.

Argumentation theory models a type of human dialog based on arguments
and conclusions. It makes explicit attacks between arguments and the
argumentation flow that leads to conclusions. A basic model in this
framework is a pair \((A,D)\), where \(A\) is a set of arguments and
\(D\) is a set of attacks among those arguments. For example, a set
\(A\) is defined as \(A = \{A1,A2,A3\}\), and a possible set of attacks
could be \(D = \{(A1,A3)\}\). Which means that if A1 is realizable then
A3 can't be realizable.

In the paper, Elrakaiby et al.~models statements given by the
stakeholders, analysts domain knowlegde and analysts inferences as
arguments, and ambiguities between them as attacks. For example, let say
the analyst listens the following statement \emph{the professor will
upload the task description within three days} (A1), but the analyst
know (domain knowlegde) that \emph{the professor may be on a business
meeting} (A2), so the analyst think (inference) that \emph{it may be
possible that it will be take longer to upload the task description}
(A3). In this scenario the set of attacks \(D\) is given by
\(D = \{(A1,A3)\}\). Thus, since there is an attack it is possible to
ask for clarifications or details.

The theorical framework proposed by Elrakaiby et al.~allows analysts to
detect and minimize ambiguities during elicitation interviews, while
most of the methods that focus on ambiguities analyze written texts. On
the other hand, this framework focuses in more complex ambiguities that
cannot be view as single terms.

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

\begin{itemize}
\tightlist
\item
  oral communication (they think it is more important than written
  texts)
\end{itemize}

\hypertarget{final-words}{%
\section{Final Words}\label{final-words}}

Nec, sodales vitae, vehicula eget, ipsum. Sed nec tortor. Aenean
malesuada. Nunc convallis, massa eu vestibulum commodo, quam mauris
interdum arcu, at pellentesque diam metus ut nulla. Vestibulum eu dolor
sit amet lacus varius fermentum. Morbi dolor enim, pulvinar eget,
lobortis ac, fringilla ac, turpis. Duis ac erat. Etiam consequat.
Integer sed est eu elit pellentesque dapibus. Duis venenatis magna
feugiat nisi. Vestibulum et turpis. Maecenas a enim. Suspendisse
ultricies ornare justo. Fusce sit amet nisi sed arcu condimentum
venenatis. Vivamus dui. Nunc accumsan, quam a fermentum mattis, magna
sapien iaculis pede, at porttitor quam odio at est.

\hypertarget{what-i-ll-focus}{%
\section{What i ll focus}\label{what-i-ll-focus}}

\begin{itemize}
\tightlist
\item
  Explain acceptance unclarity
\item
  Explain Dung's framework
\item
  Explain ASPIC+
\item
  Inconsistencies
\item
  It's higly influenced by the domain knowledge of the analyst
\end{itemize}

\hypertarget{my-idea}{%
\subsection{My idea}\label{my-idea}}

\begin{itemize}
\item
  knowledge domain has influence
\item
  analyst domain knowledge is statiscally relevant
\item
  analyst training is even more relevant
\item
  influence of tacit knowlegde in interviews
\item
  ambiguity in interviews - focus on interviewer must have domain
  knowledge
\item
  what i want to do is : possible beneficts in requirement elicitaiton
  is usings two techniques based on the domain knowledge of the analyst,
  sometimes it is good to have an expert and an ignorant of a topic .
\item
  limitations of the technique based on domain knowlegde and tacit
  knowlegde.
\item
  how types of tacit knowlegde may influence in the proposal theory
\item
  how domain knowlegde may influence in the proposal theory
\item
  As an intro:

  \begin{itemize}
  \tightlist
  \item
    analyst domain knowledge is statiscally relevant
  \item
    analyst training is even more relevant
  \end{itemize}
\item
  focus on the technique from the perspective of knowlegde and technique
\item
  future of that technique to solve more complex problems, from the
  prospective of knowlegde and technique
\end{itemize}

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-elrakaiby2017using}{}%
{[}1{]} Y. Elrakaiby, A. Ferrari, P. Spoletini, S. Gnesi, and B.
Nuseibeh, ``Using argumentation to explain ambiguity in requirements
elicitation interviews,'' in \emph{Requirements engineering conference
(re), 2017 ieee 25th international}, 2017, pp. 51--60.

\end{document}

### 2018-01-02 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

@@
 
-\hypertarget{conclusion}{%
-\subsection{Conclusion}\label{conclusion}}
+\hypertarget{effect-of-domain-knowledge-on-elicitation-effectiveness-an-internally-replicated-controlled-experiment}{%
+\section{Effect of Domain Knowledge on Elicitation Effectiveness: An
+Internally Replicated Controlled
+Experiment}\label{effect-of-domain-knowledge-on-elicitation-effectiveness-an-internally-replicated-controlled-experiment}}
 
-\begin{itemize}
-\tightlist
-\item
-  oral communication (they think it is more important than written
-  texts)
-\end{itemize}
+The effectiveness of elicitation interviews may be influenced by analyst
+skills or characteristics. In these high intensive oral communication
+scenario the analyst must be able to draw out relevant information and
+needs from the stakeholders. It has been reported that the effectiveness
+of the interviews has a direct relation with the domain knowlegde of the
+analyst. However, there are also studies suggesting that in somecases
+the domain knowlegde have negatives effects in the effectiveness of
+interviews.
 
-\hypertarget{final-words}{%
-\section{Final Words}\label{final-words}}
+In this paper {[}2{]}, Aranda et al.~studied the influence of the
+analyst domain knowlegde on the effectiveness of elicitation interviews.
+The main question they tried to answer was
 
-Nec, sodales vitae, vehicula eget, ipsum. Sed nec tortor. Aenean
-malesuada. Nunc convallis, massa eu vestibulum commodo, quam mauris
-interdum arcu, at pellentesque diam metus ut nulla. Vestibulum eu dolor
-sit amet lacus varius fermentum. Morbi dolor enim, pulvinar eget,
-lobortis ac, fringilla ac, turpis. Duis ac erat. Etiam consequat.
-Integer sed est eu elit pellentesque dapibus. Duis venenatis magna
-feugiat nisi. Vestibulum et turpis. Maecenas a enim. Suspendisse
-ultricies ornare justo. Fusce sit amet nisi sed arcu condimentum
-venenatis. Vivamus dui. Nunc accumsan, quam a fermentum mattis, magna
-sapien iaculis pede, at porttitor quam odio at est.
+\emph{Does analyst domain knowledge influence (either positively or
+negatively) the effectiveness of the requirements elicitation activity?}
 
-\hypertarget{what-i-ll-focus}{%
-\section{What i ll focus}\label{what-i-ll-focus}}
+For this purpose, the authors performed the study in two stages. They
+performed an initial baseline experiment with two domain problems, and
+then they performed an internal replication with two other domain
+problems. Furthermore, the authors divided the elicitation process in
+two phases. The elication phase which is the actual interview with the
+stakeholder, and the reporting phase in which the analyst understands
+and documents the information gathered in the elication phase.
 
-\begin{itemize}
-\tightlist
-\item
-  Explain acceptance unclarity
-\item
-  Explain Dung's framework
-\item
-  Explain ASPIC+
-\item
-  Inconsistencies
-\item
-  It's higly influenced by the domain knowledge of the analyst
-\end{itemize}
+One remark of the study is that the authors chose students because of
+their lack of experience in eliciation interviews, isolation of the
+domain knowledge, and to analyze, in the internal replication, the
+influence of the training in requirements engineering in eliciation
+interviews. In the study participated post-graduated students as
+interviewers and two professors as interviewees. The students should
+make open interviews and elicitate the information afterwards. Moreover,
+for each domain problem the students were separeted in two groups based
+on their level of domain knowlegde, \emph{domain-aware} and
+\emph{domain-ignorant}. On the other hand, the effectiveness of the
+elicitations was based on the comparison between the number of concepts,
+processes and requirements elicitated by the students and the
+benchmarks.
+
+The results of the baseline experiment suggest that the domain knowlegde
+of the analysts has no significant influence in the effectiveness of the
+elicitation interviews. However, the results also suggest that the
+domain knowlegde of the interviewees has statistically significant
+influence. Supplementary, the results of the internal replication also
+suggest that the domain knowlegde of the stakeholders is more relevant
+than the analysts', in term of effectiveness of the elicitation
+interviews. Nevertheless, these results also show that the possitive
+effects of the training in requirements engineering of the interviewers,
+with these effects beiang as relevant as interviwees' domain knowlegde.
+
+\hypertarget{what-ill-do}{%
+\section{What i'll do}\label{what-ill-do}}
+
+Explain acceptance unclarity Explain Dung's framework Explain ASPIC+
+Inconsistencies It's higly influenced by the domain knowledge of the
+analyst
 
@@
 
-\begin{itemize}
-\item
-  knowledge domain has influence
-\item
-  analyst domain knowledge is statiscally relevant
-\item
-  analyst training is even more relevant
-\item
-  influence of tacit knowlegde in interviews
-\item
+knowledge domain has influence analyst domain knowledge is statiscally
+relevant analyst training is even more relevant influence of tacit
+knowlegde in interviews
+
 ambiguity in interviews - focus on interviewer must have domain
-  knowledge
-\item
-  what i want to do is : possible beneficts in requirement elicitaiton
-  is usings two techniques based on the domain knowledge of the analyst,
-  sometimes it is good to have an expert and an ignorant of a topic .
-\item
+knowledge what i want to do is : possible beneficts in requirement
+elicitaiton is usings two techniques based on the domain knowledge of
+the analyst, sometimes it is good to have an expert and an ignorant of a
+topic .
+
 limitations of the technique based on domain knowlegde and tacit
-  knowlegde.
-\item
-  how types of tacit knowlegde may influence in the proposal theory
-\item
-  how domain knowlegde may influence in the proposal theory
-\item
-  As an intro:
+knowlegde. how types of tacit knowlegde may influence in the proposal
+theory how domain knowlegde may influence in the proposal theory
 
-  \begin{itemize}
-  \tightlist
-  \item
-    analyst domain knowledge is statiscally relevant
-  \item
-    analyst training is even more relevant
-  \end{itemize}
-\item
-  focus on the technique from the perspective of knowlegde and technique
-\item
-  future of that technique to solve more complex problems, from the
-  prospective of knowlegde and technique
-\end{itemize}
+As an intro: analyst domain knowledge is statiscally relevant analyst
+training is even more relevant focus on the technique from the
+perspective of knowlegde and technique future of that technique to solve
+more complex problems, from the prospective of knowlegde and technique
 
@@
 
+\leavevmode\hypertarget{ref-aranda2016effect}{}%
+{[}2{]} A. M. Aranda, O. Dieste, and N. Juristo, ``Effect of domain
+knowledge on elicitation effectiveness: An internally replicated
+controlled experiment,'' \emph{IEEE Transactions on Software
+Engineering}, vol. 42, no. 5, pp. 427--451, 2016.
+
 \end{document}

### 2018-01-03 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

@@
 
+\hypertarget{requirements-elicitation-towards-the-unknown-unknowns}{%
+\section{Requirements elicitation: Towards the Unknown
+Unknowns}\label{requirements-elicitation-towards-the-unknown-unknowns}}
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+Abstract---Requirements elicitation research is reviewed using a
+framework categorising the relative `knowness' of requirements
+specification and Common Ground discourse theory. The main contribution
+of this survey is to review requirements elicitation from the
+perspective of this framework and propose a road map of research to
+tackle outstanding elicitation problems involving tacit knowledge. The
+paper concludes with remarks on the possibility of elicitation tackling
+the most difficult question of `unknown unknown' requirements.
+
+However, elicitation still remains problematic; missing or mistaken
+requirements still delay projects and cause cost overruns in this paper
+we set out to explore the field from the perspective made famous from
+Donald Rumsfeld's quote of the ``known knowns, the known unknowns, and
+unknown unknowns''. This perspective poses challenges to requirements
+elicitation since it probes the boundaries of knowledge and who
+possesses it, thereby creating a useful stress test for requirements
+elicitation techniques, methods and tools.
+
+Elicitation review framework (ERF). Tacit knowledge taxonomy based on
+the properties of \emph{expressible} (know knowledge),
+\emph{articulated} (documented domain knowledge), \emph{accesible} (need
+memory recall), \emph{relevant} to the project: • Known knowns:
+expressible, articulated, and relevant. • Known unknowns: not
+expressible or articulated, but accessible and potentially relevant. •
+Unknown knowns: potentially accessible but not articulated. • Unknown
+unknowns: not expressible, articulated or accessible but still
+potentially relevant.
+
+From the perspective of the analyst/ stakeholder: - Known knowns: not a
+problem - known unknowns: the analyst has a domain knowlegde but the
+stakeholder may forgot or be unaware - Unknown knowns: the stakeholder
+holds a knowlegde but it is not articulated, so the analyst has to
+discover this tacit knowlegde and elicitate it. Once the stakeholder
+shows a glimpse of his knowlegde the analyst realize that there is
+something and the problem into known unknowns. - Unknown unknowns: the
+analist and the stakeholder are unaware of what's missing, but it has
+the potential to be relevant information.
+
+The Tacit Knowledge Framework {[}14{]} poses three challenges: (i)
+Identifying tacit knowledge: the unknown knowns; even when the analyst
+suspects they exist (known unknowns), making tacit knowledge accessible
+may not be easy. (ii) Knowing what is relevant and should be articulated
+from the analyst's perspective: the necessary detail problem. (iii)
+Articulating the knowledge where it is needed, in the correct context,
+so it can be understood by all stakeholders.
+
+The first step to solve the problem of unknown unknowns is to assume
+that may exist a missing knowledge, and being prepared to invest in
+order to find it. The goal is to convert the unknown unknowns into known
+knowns.
+
+Common ground theory explains how meaning is constructed by conversation
+and action, which progresses towards a mutually agreed goal.
+
+Action Ladder and Project: Meaning in conversations has different
+layers: the surface of explicit expression, tacit knowlegde and
+linguistic interpretation. Setting: where the conversation takes place
+(time, location, domain knowledge) Arena: shared knowledge about the
+culture, norms, history and assumptions which allow dialogue between
+people to be interpreted in their context.
+
+For our purposes, Common Ground contributes `tools for thought' which
+can address the unknowns problems. For example the Arena suggests
+questions to discover more detail of the users' background which may
+uncover unknown concerns (viz cultural, political issues);
+
+For many techniques the ability to detect the known unknowns depends on
+the analyst's plan and the sampling strategy. In the case of interviews
+the ability to dectect unknown unknowns depends on the follow-up
+questions and sample size. Also interviews since they depends on natural
+language communication there is always the possibility of ambiguous
+interpretations.
+
+Interviews approach natural human conversation so they support the
+dynamic construction of understanding and exploration of the Arena and
+Setting of the dialogue by explicit questions and observation. However,
+interviews are weaker for reflection(reflection as an intentional,
+active progression of learning), where the analyst has to rely on notes
+and recordings. Furthermore, eliciting tacit knowledge depends on the
+analysts' questioning skills interaction. Hence a combination of
+techniques rather than structured interviews per se is probably the most
+effective approach. .
+
+There are four research directions to push the boundaries of the
+unknown: Unknown knowns. The problem for the analyst is discovering what
+the stakeholder knows but does not articulate. Sensitivity to political
+issues, user values and emotions needs to be researched in depth to
+provide `emotional intelligence' guidance for analysts so they can
+anticipate these unknowns and elicit sensitive tacit knowledge. The
+Common Ground quest is to be more sensitive to the stakeholder's
+Setting, feelings, norms and culture
+
+Known unknowns. In this case the analyst has some awareness of the
+necessary knowledge, so an agenda for elicitation can be set. Most
+techniques involve exploring the implications of the system-domain
+boundary. Challenging assumptions, reasoning about the implications of
+obstacles, and relaxing domain constraints need further research towards
+not only hard influences, but also soft, probabilistic implications.
+
+Design discovery. This is a variant of known unknowns where the
+challenge is to solve the ``I'll know what I want when I see it''
+problem. Much progress has been made in this area with prototypes,
+storyboards and mock-ups; however, simulations and virtual worlds may
+have further potential.
+
+Unknown unknowns. Two approaches could address elicitation of
+`over-the-horizon' knowledge. First, creative RE, which is already
+established {[}55{]}, needs to be integrated with social media, so that
+collaborative creative RE is empowered. This could involve designing
+socio- technical elicitation systems, as e-communities, communities of
+practice with global distributions for the increasing number of Internet
+applications. Secondly, the use of analogies and examples, and also
+counter examples, can challenge the boundaries of the possible to
+develop new design ideas.
+
+Known unknowns imply the need for exploration of the problem and
+solution spaces; (e.g.) using a combination of obstacle anaylsis and
+prototyping.
+
 \hypertarget{what-ill-do}{%

### 2018-01-03 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

--- 2018-01-02 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
@@
 One of the major causes of ambiguities in elicitation interviews is the
-prescense of tacit knowlegde. In some cases ambiguities can't be always
+presence of tacit knowledge. In some cases ambiguities can't be always
 be explained as separated term, sometimes it is required to have a
-context. Even under these circunstances, the analyst must be able to
-identify and alleviate them in order to elicitate relevant information
-of the system. For this purpose it is necessary to provide the analyst
-with proper tools. In this paper Yehia Elrakaiby et al. {[}1{]} proposed
-a theorical framework to overcome ambiguity during interviews in the
+context. Even under these circumstances, the analyst must be able to
+identify and alleviate them in order to elicit relevant information of
+the system. For this purpose it is necessary to provide the analyst with
+proper tools. In this paper Yehia Elrakaiby et al. {[}1{]} proposed a
+theoretical framework to overcome ambiguity during interviews in the
 elicitation phase. The framework is based on the ``Argumentation
@@
 In that sense, Elrakaiby et al.~focus on one type of ambiguities, the
-``acceptance unclarity''. An acceptance unclarity occurs everytime the
+``acceptance unclarity''. An acceptance unclarity occurs every time the
 analyst is able to assign an interpretation or meaning to the speech
@@
 comprehend the problem, or analysts identify inconsistencies with their
-current understanding of the problem or domain knowlegde. By using
+current understanding of the problem or domain knowledge. By using
 argumentation theory framework, statements and ambiguities can be
-characterized as ``arguments'' and ``attacks'' respectevely.
+characterized as ``arguments'' and ``attacks'' respectively.
 
@@
 In the paper, Elrakaiby et al.~models statements given by the
-stakeholders, analysts domain knowlegde and analysts inferences as
+stakeholders, analysts domain knowledge and analysts inferences as
 arguments, and ambiguities between them as attacks. For example, let say
@@
 upload the task description within three days} (A1), but the analyst
-know (domain knowlegde) that \emph{the professor may be on a business
+know (domain knowledge) that \emph{the professor may be on a business
 meeting} (A2), so the analyst think (inference) that \emph{it may be
@@
 
-The theorical framework proposed by Elrakaiby et al.~allows analysts to
-detect and minimize ambiguities during elicitation interviews, while
+The theoretical framework proposed by Elrakaiby et al.~allows analysts
+to detect and minimize ambiguities during elicitation interviews, while
 most of the methods that focus on ambiguities analyze written texts. On
@@
 needs from the stakeholders. It has been reported that the effectiveness
-of the interviews has a direct relation with the domain knowlegde of the
-analyst. However, there are also studies suggesting that in somecases
-the domain knowlegde have negatives effects in the effectiveness of
+of the interviews has a direct relation with the domain knowledge of the
+analyst. However, there are also studies suggesting that in some cases
+the domain knowledge have negatives effects in the effectiveness of
 interviews.
@@
 In this paper {[}2{]}, Aranda et al.~studied the influence of the
-analyst domain knowlegde on the effectiveness of elicitation interviews.
+analyst domain knowledge on the effectiveness of elicitation interviews.
 The main question they tried to answer was
@@
 problems. Furthermore, the authors divided the elicitation process in
-two phases. The elication phase which is the actual interview with the
+two phases. The elicitation phase which is the actual interview with the
 stakeholder, and the reporting phase in which the analyst understands
-and documents the information gathered in the elication phase.
+and documents the information gathered in the elicitation phase.
 
 One remark of the study is that the authors chose students because of
-their lack of experience in eliciation interviews, isolation of the
+their lack of experience in elicitation interviews, isolation of the
 domain knowledge, and to analyze, in the internal replication, the
-influence of the training in requirements engineering in eliciation
+influence of the training in requirements engineering in elicitation
 interviews. In the study participated post-graduated students as
 interviewers and two professors as interviewees. The students should
-make open interviews and elicitate the information afterwards. Moreover,
-for each domain problem the students were separeted in two groups based
-on their level of domain knowlegde, \emph{domain-aware} and
+make open interviews and elicit the information afterwards. Moreover,
+for each domain problem the students were separated in two groups based
+on their level of domain knowledge, \emph{domain-aware} and
 \emph{domain-ignorant}. On the other hand, the effectiveness of the
-elicitations was based on the comparison between the number of concepts,
-processes and requirements elicitated by the students and the
+elicitation's was based on the comparison between the number of
+concepts, processes and requirements elicited by the students and the
 benchmarks.
 
-The results of the baseline experiment suggest that the domain knowlegde
+The results of the baseline experiment suggest that the domain knowledge
 of the analysts has no significant influence in the effectiveness of the
 elicitation interviews. However, the results also suggest that the
-domain knowlegde of the interviewees has statistically significant
+domain knowledge of the interviewees has statistically significant
 influence. Supplementary, the results of the internal replication also
-suggest that the domain knowlegde of the stakeholders is more relevant
+suggest that the domain knowledge of the stakeholders is more relevant
 than the analysts', in term of effectiveness of the elicitation
-interviews. Nevertheless, these results also show that the possitive
+interviews. Nevertheless, these results also show that the positive
 effects of the training in requirements engineering of the interviewers,
-with these effects beiang as relevant as interviwees' domain knowlegde.
+with these effects being as relevant as interviewees' domain knowledge.
+
+\hypertarget{requirements-elicitation-towards-the-unknown-unknowns}{%
+\section{Requirements elicitation: Towards the Unknown
+Unknowns}\label{requirements-elicitation-towards-the-unknown-unknowns}}
+
+Elicitation in requirements engineering is still problematic because
+missing or mistaken requirements are hard to elicit, and this produce
+projects delays and have financial implications. In this paper, the
+authors propose an elicitation review framework (ERF) in order to
+explore the different challenges related to the ``unknowness'' of the
+domain knowledge. Therefore, proposing a road map of research to tackle
+the different levels of the ``unknowness''.
+
+The authors made use of the properties of \emph{expressible} (know
+knowledge), \emph{articulated} (documented domain knowledge),
+\emph{accessible} (need memory recall), \emph{relevant} (to the
+project). With these four properties, authors definied the following
+levels of unknowness in domain knowledge.
+
+\begin{itemize}
+\tightlist
+\item
+  Known knowns: knowledge that is expressible, articulated, and
+  relevant.
+\item
+  Known unknowns: knowledge that is not expressible or articulated, but
+  accessible and potentially relevant.
+\item
+  Unknown knowns: knownledge that is potentially accessible but not
+  articulated.
+\item
+  Unknown unknowns: knownledge that is not expressible, articulated nor
+  accessible but may be relevant.
+\end{itemize}
+
+This levels of knownledge implies problems of different perspective of
+the elicitation process that involves analysts and stakeholders. The
+\emph{known knowns} is a simple scenario since the counterparts are
+aware of the domain problem which is expressable and articulated. In the
+case of the \emph{known unknowns}, the analysts has a domain knowledge
+and they should be able draw out the information from the stakeholders
+that they might be unaware of. In contrast, in the \emph{unknow knowns}
+scenario the stakeholders are the ones that are aware of the domain
+knowledge but for some reason it is no articulated, and therfore, the
+analysts once they notice any glimpse of the stakeholders information
+they should able to discover and elicit that. On the other hand, in the
+case of \emph{unknows unknowns} both counterparts are unaware of the
+missing information that might be relevant to the system.
+
+Based on the perspectives described before, the authors identified three
+challenges to requirement elicitation. The first one is to identifying
+tacit knowledge (unknown knowns), even in the case the analyst presume
+it exist (known unknowns). The second challenge is that the analyst
+should know what is relevant and should be articulated. And the last one
+is the articulation of the knowledge. Thus, in the worst case scenario
+the goal is go from the unknow unknows perspective to know knows.
+
+Finally, the authors suggest four research directions to deal with the
+unknowness problem. Starting with the known unknown in which the analyst
+should challenging assumptions, implications, and relaxing domain
+constrains in order to increase the probability to elicit the unaware
+knownledge of the stakeholders. In the same direction, in the design
+discovery, which is a variant of the latter case, the analyst should
+deal with the the following statement ``I'll know what I want when I see
+it''. Thus, there is a need of prototyping or simulations as part of the
+elicitation process. In the case of the unknown knowns in which the
+analyst can elicit tacit knownledge by taking into account the
+background (political, cultural, emotional) of stakeholders, and use
+that background as an ``emotional guidance'' in order to draw out the
+relevant information. Finally, in the case of unknown unknows the
+authors suggest to main approaches. The first one is based on the
+``over-the-horizon'' knowledge, in which authors proposed a
+socio-technical approach based on social media and e-communities. And
+the other one is using counter examples that can challenges the
+boundaries of the idea under development.
 
@@
 Explain acceptance unclarity Explain Dung's framework Explain ASPIC+
-Inconsistencies It's higly influenced by the domain knowledge of the
+Inconsistencies It's highly influenced by the domain knowledge of the
 analyst
@@
 
-knowledge domain has influence analyst domain knowledge is statiscally
+knowledge domain has influence analyst domain knowledge is statistically
 relevant analyst training is even more relevant influence of tacit
-knowlegde in interviews
+knowledge in interviews
 
 ambiguity in interviews - focus on interviewer must have domain
-knowledge what i want to do is : possible beneficts in requirement
-elicitaiton is usings two techniques based on the domain knowledge of
-the analyst, sometimes it is good to have an expert and an ignorant of a
+knowledge what i want to do is : possible benefits in requirement
+elicitation is using two techniques based on the domain knowledge of the
+analyst, sometimes it is good to have an expert and an ignorant of a
 topic .
 
-limitations of the technique based on domain knowlegde and tacit
-knowlegde. how types of tacit knowlegde may influence in the proposal
-theory how domain knowlegde may influence in the proposal theory
+limitations of the technique based on domain knowledge and tacit
+knowledge. how types of tacit knowledge may influence in the proposal
+theory how domain knowledge may influence in the proposal theory
 
-As an intro: analyst domain knowledge is statiscally relevant analyst
+As an intro: analyst domain knowledge is statistically relevant analyst
 training is even more relevant focus on the technique from the
-perspective of knowlegde and technique future of that technique to solve
-more complex problems, from the prospective of knowlegde and technique
+perspective of knowledge and technique future of that technique to solve
+more complex problems, from the prospective of knowledge and technique
 

### 2018-01-05 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

@@
             pdfauthor={Daniel Paredes},
-            pdftitle={The power of dark silicon},
+            pdftitle={I need a title},
             colorlinks=true,
@@
 
-\title{The power of dark silicon}
+\title{I need a title}
 \author{Daniel Paredes}
@@
 \begin{abstract}
-Sit amet mauris. Curabitur a quam. Aliquam neque. Nam nunc nunc, lacinia
-sed, varius quis, iaculis eget, ante. Nulla dictum justo eu lacus.
-Phasellus sit amet quam. Nullam sodales. Cras non magna eu est
-consectetuer faucibus. Donec tempor lobortis turpis. Sed tellus velit,
-ullamcorper ac, fringilla vitae, sodales nec, purus. Morbi aliquet risus
-in mi.
+I need an abstract
+aeuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuu
 
@@
 I need an introduction\ldots{}
+
+\hypertarget{unknowness}{%
+\section{Unknowness}\label{unknowness}}
+
+Requirements elicitation is the process of finding and formulation
+requirements, and this process has many barriers due to stakeholders are
+not able to express their needs, explain what they do and why,
+conflicting demands, or new demands once other are met{[}1{]}, just to
+mention some examples. Many analyst consider interviews the most
+important elicitation technique, and usually elicitation process starts
+with interviewing the stakeholders. Interviews allow analysts to check
+their understanding about the problem domain inmediately and ask for
+clarifications. Moreover, this technique is versatile in the sense of it
+is possible that new and unexpected issues come up and they can be
+attacked at that moment.
+
+However, elicit tacit knowledge in interviews is still a hard task to
+do. This tacit knowledge can be classified in four groups as describe in
+{[}2{]}. The \textbf{known knowns}, \textbf{known unknowns},
+\textbf{unknown knowns} and \textbf{unknown unknowns}. The known knowns
+is the knowledge that is documented, expressible, and relevant to the
+system. In order words, is the scenario in which it is possible to
+elicit since the beginning all the requirements, there is no tacit
+knowledge. The known unknowns is the knowledge that cannot be
+expressible because the stakeholders are not aware of their lack of
+domain knowledge, their might forget it. In this case analyst are aware
+of the domain knowledge and therefore, their job is to challenge
+assumptions or implications. The unknown knowns is the knowledge that
+stakeholders hold but it is not documented by some reason. Thus,
+analysts should use their interviewing skill to elicit when they spot
+any glimpse of that knowledge. The unknown unknowns is the knowledge
+that neither the analysts nor stakeholders are aware.
 
@@
 the system. For this purpose it is necessary to provide the analyst with
-proper tools. In this paper Yehia Elrakaiby et al. {[}1{]} proposed a
+proper tools. In this paper Yehia Elrakaiby et al. {[}3{]} proposed a
 theoretical framework to overcome ambiguity during interviews in the
@@
 
-In this paper {[}2{]}, Aranda et al.~studied the influence of the
+In this paper {[}4{]}, Aranda et al.~studied the influence of the
 analyst domain knowledge on the effectiveness of elicitation interviews.
@@
 
-The authors made use of the properties of \emph{expressible} (know
+The authors made use of the properties of \emph{expressible} (known
 knowledge), \emph{articulated} (documented domain knowledge),
 \emph{accessible} (need memory recall), \emph{relevant} (to the
-project). With these four properties, authors definied the following
+project). With these four properties, authors defined the following
 levels of unknowness in domain knowledge.
@@
 \item
-  Unknown knowns: knownledge that is potentially accessible but not
+  Unknown knowns: knowledge that is potentially accessible but not
   articulated.
 \item
-  Unknown unknowns: knownledge that is not expressible, articulated nor
+  Unknown unknowns: knowledge that is not expressible, articulated nor
   accessible but may be relevant.
@@
 
-This levels of knownledge implies problems of different perspective of
+This levels of knowledge implies problems of different perspective of
 the elicitation process that involves analysts and stakeholders. The
 \emph{known knowns} is a simple scenario since the counterparts are
-aware of the domain problem which is expressable and articulated. In the
+aware of the domain problem which is expressible and articulated. In the
 case of the \emph{known unknowns}, the analysts has a domain knowledge
 and they should be able draw out the information from the stakeholders
-that they might be unaware of. In contrast, in the \emph{unknow knowns}
+that they might be unaware of. In contrast, in the \emph{unknown knowns}
 scenario the stakeholders are the ones that are aware of the domain
-knowledge but for some reason it is no articulated, and therfore, the
+knowledge but for some reason it is no articulated, and therefore, the
 analysts once they notice any glimpse of the stakeholders information
 they should able to discover and elicit that. On the other hand, in the
-case of \emph{unknows unknowns} both counterparts are unaware of the
+case of \emph{unknown unknowns} both counterparts are unaware of the
 missing information that might be relevant to the system.
@@
 is the articulation of the knowledge. Thus, in the worst case scenario
-the goal is go from the unknow unknows perspective to know knows.
+the goal is go from the unknown unknowns perspective to known knowns.
 
@@
 constrains in order to increase the probability to elicit the unaware
-knownledge of the stakeholders. In the same direction, in the design
+knowledge of the stakeholders. In the same direction, in the design
 discovery, which is a variant of the latter case, the analyst should
@@
 elicitation process. In the case of the unknown knowns in which the
-analyst can elicit tacit knownledge by taking into account the
-background (political, cultural, emotional) of stakeholders, and use
-that background as an ``emotional guidance'' in order to draw out the
-relevant information. Finally, in the case of unknown unknows the
+analyst can elicit tacit knowledge by taking into account the background
+(political, cultural, emotional) of stakeholders, and use that
+background as an ``emotional guidance'' in order to draw out the
+relevant information. Finally, in the case of unknown unknowns the
 authors suggest to main approaches. The first one is based on the
@@
 
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
+
+I need some conclusions
+
 \hypertarget{what-ill-do}{%
@@
 
-Explain acceptance unclarity Explain Dung's framework Explain ASPIC+
-Inconsistencies It's highly influenced by the domain knowledge of the
-analyst
-
-\hypertarget{my-idea}{%
-\subsection{My idea}\label{my-idea}}
-
-knowledge domain has influence analyst domain knowledge is statistically
-relevant analyst training is even more relevant influence of tacit
-knowledge in interviews
-
-ambiguity in interviews - focus on interviewer must have domain
-knowledge what i want to do is : possible benefits in requirement
-elicitation is using two techniques based on the domain knowledge of the
-analyst, sometimes it is good to have an expert and an ignorant of a
-topic .
-
-limitations of the technique based on domain knowledge and tacit
-knowledge. how types of tacit knowledge may influence in the proposal
-theory how domain knowledge may influence in the proposal theory
-
-As an intro: analyst domain knowledge is statistically relevant analyst
-training is even more relevant focus on the technique from the
-perspective of knowledge and technique future of that technique to solve
-more complex problems, from the prospective of knowledge and technique
+Explain tacit knowledge explain domain knowledge Explain acceptance
+unclarity Explain Dung's framework Explain ASPIC+ Inconsistencies It's
+highly influenced by the domain knowledge of the analyst
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-lauesen2001softwarereq}{}%
+{[}1{]} S. Lauesen, \emph{Software requirements: Styles and techniques},
+1st ed. Pearson Education, 2001.
+
+\leavevmode\hypertarget{ref-sutcliffe2013requirements}{}%
+{[}2{]} A. Sutcliffe and P. Sawyer, ``Requirements elicitation: Towards
+the unknown unknowns,'' in \emph{Requirements engineering conference
+(re), 2013 21st ieee international}, 2013, pp. 92--104.
+
 \leavevmode\hypertarget{ref-elrakaiby2017using}{}%
-{[}1{]} Y. Elrakaiby, A. Ferrari, P. Spoletini, S. Gnesi, and B.
+{[}3{]} Y. Elrakaiby, A. Ferrari, P. Spoletini, S. Gnesi, and B.
 Nuseibeh, ``Using argumentation to explain ambiguity in requirements
@@
 \leavevmode\hypertarget{ref-aranda2016effect}{}%
-{[}2{]} A. M. Aranda, O. Dieste, and N. Juristo, ``Effect of domain
+{[}4{]} A. M. Aranda, O. Dieste, and N. Juristo, ``Effect of domain
 knowledge on elicitation effectiveness: An internally replicated

### 2018-01-05 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

@@
 I need an abstract
-aeuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuu
 
 % lncs keyword extension 
-\keywords{hope, luke, ewoks}
+\keywords{I, need, keywords}
 
@@
 
-\hypertarget{unknowness}{%
-\section{Unknowness}\label{unknowness}}
+\hypertarget{my-approach-i-need-a-section-title}{%
+\section{My approach (i need a section
+title)}\label{my-approach-i-need-a-section-title}}
+
+\hypertarget{tacit-knowledge-in-elicitation-interviews}{%
+\subsection{Tacit knowledge in elicitation
+interviews}\label{tacit-knowledge-in-elicitation-interviews}}
 
@@
 with interviewing the stakeholders. Interviews allow analysts to check
-their understanding about the problem domain inmediately and ask for
+their understanding about the problem domain immediately and ask for
 clarifications. Moreover, this technique is versatile in the sense of it
@@
 that neither the analysts nor stakeholders are aware.
+
+\hypertarget{challenge-tacit-knowledge}{%
+\subsection{Challenge tacit knowledge}\label{challenge-tacit-knowledge}}
+
+The unknowness clarification presented in above suggest the presence of
+three problems. The goal is to go from any scenario in which tacit
+knowledge exists to known knowns. In order to achieve that goal and take
+the advantages presented in elicitation interviews (immediately
+clarification of assumptions and debate of implications) we are going to
+use the theoretical framework described by Elrakaiby {[}3{]}. In this
+framework we model the interview as a set of arguments and attacks
+between them. In that sense, we will able to spot ambiguities and tacit
+knowledge in terms of inconsistencies and insufficiency of information.
+We will adapt some examples from {[}3{]} to show how each tacit
+knowledge scenario can be addresed.
+
+\textbf{known unknowns}: In the following example the domain knowledge
+of the analyst is used to detect inconsistencies (attacks), because the
+stakeholder didn't take into account relevant information about domain
+application (location of trash bins).
+
+A customers wants a recycling-support system and one of the goals is
+\emph{to avoid fines from the municipality for incorrect recycling}.
+According to the domain knowledge of the analyst, \emph{trash bins are
+placed along the streets}. Thus, the goal is inconsistent with the
+domain knowledge of the analyst because \emph{there is no way to trace
+back person who brakes the recycling rule}. This scenario can be modeled
+using arguments and attacks as follows:
+
+The arguments: (A1)trash bins are placed along the streets, (A2)since
+trash bins are placed along the streets, the trash owner cannot be
+traced back. (B1)people who do not recycle should be fined (B2)to fine
+people, the municipality must be able to trace products in trash bins
+back to their owners.
+
+Attacks: A2 attacks B1, and viceversa.
+
+\textbf{unknown knowns}: In the following example analyst challenges the
+stakeholder statement by using a question, as a result the stakeholder
+reveals new information (reply).
+
+A customers wants to develop a system to allow patients to measure the
+amount of glucose in their blood, and then send the result to their
+general practitioner. If the glucose level is above a certain threshold,
+the practitioner pays a visit to the patient. The customer says:
+\emph{In one-two days the doctor sees the notification in the system}.
+Then analyst asks: \emph{What happens if the doctor is not available for
+any reason?}. The customer replies: \emph{The general practitioner is
+substituted by another doctor who accesses the same system}.
+
+The arguments: (A1)in one-two days the doctor sees the
+notification,(B1)the doctor might be unavailable,(B2)since the the
+doctor might be unavailable, the notification might be delayed.
+
+The attacks: A1 attacks B2, and viceversa
+
+\textbf{unknown unknowns}: In the following example the stakeholder
+didn't notice the inconsistency between his statements, but the analyst
+did and asked for clarification. However, the stakeholder couldn't give
+an answers due to his ignorance.
+
+One of the customers wants to develop an app to manage medical-related
+reservation in Tuscani. The costumer mentions that the \emph{current
+reservation system, based on phone calls, was centralised}. During the
+interview, the customer says that \emph{depending on where the
+examination/visit will be, the patient has to call Nottola or Siena}.
+The analyst could not understand how this realization was possible since
+it means that the reservation system is not centralized. So the analyst
+asks for clarification and the stakeholder cannot give any acceptable
+answer.
+
+The arguments: (A1)the current reservation is centralized, (B1)depending
+on where the examination/visit will be (B2)the patience has to call
+Nottola or Siena, (B3) since it is possible to call either Nottola or
+Siena the system is not centralized.
+
+The attacks: A1 attacks B3, and viceversa
+
+\hypertarget{limits-of-elicited-knowledge}{%
+\subsection{Limits of elicited
+knowledge}\label{limits-of-elicited-knowledge}}
+
+aeu
 

### 2018-01-05 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

@@
 \IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+\usepackage{longtable,booktabs}
 \ifxetex
@@
 
-A customers wants a recycling-support system and one of the goals is
+A customers wanted a recycling-support system and one of the goals was
 \emph{to avoid fines from the municipality for incorrect recycling}.
 According to the domain knowledge of the analyst, \emph{trash bins are
-placed along the streets}. Thus, the goal is inconsistent with the
+placed along the streets}. Thus, the goal was inconsistent with the
 domain knowledge of the analyst because \emph{there is no way to trace
@@
 \textbf{unknown knowns}: In the following example analyst challenges the
-stakeholder statement by using a question, as a result the stakeholder
-reveals new information (reply).
+stakeholder statement, as a result the stakeholder reveals new
+information (reply).
 
@@
 general practitioner. If the glucose level is above a certain threshold,
-the practitioner pays a visit to the patient. The customer says:
-\emph{In one-two days the doctor sees the notification in the system}.
-Then analyst asks: \emph{What happens if the doctor is not available for
-any reason?}. The customer replies: \emph{The general practitioner is
-substituted by another doctor who accesses the same system}.
+the practitioner pays a visit to the patient. The customer said:
+\emph{in one-two days the doctor sees the notification in the system}.
+Then analyst asked: \emph{What happens if the doctor is not available
+for any reason?}. The customer replied: \emph{The general practitioner
+is substituted by another doctor who accesses the same system}.
 
@@
 One of the customers wants to develop an app to manage medical-related
-reservation in Tuscani. The costumer mentions that the \emph{current
+reservation in Tuscani. The costumer mentioned that the \emph{current
 reservation system, based on phone calls, was centralised}. During the
-interview, the customer says that \emph{depending on where the
+interview, the customer said that \emph{depending on where the
 examination/visit will be, the patient has to call Nottola or Siena}.
 The analyst could not understand how this realization was possible since
-it means that the reservation system is not centralized. So the analyst
-asks for clarification and the stakeholder cannot give any acceptable
-answer.
+it means the reservation system is not centralized. Therefore the
+analyst asked for clarification and the stakeholder couldn't give any
+acceptable answer.
 
@@
 
-aeu
+In the last section we present how to use a theoretical framework based
+on arguments and attacks to addresed the different levels of tacit
+knowledge. In this section we will compare in which scenario of tacit
+knowledge the elicitation interview is more effective based on Aranda et
+al.~work {[}4{]} about the effect of domain knowledge on elicitation
+process.\\
+Effectiveness is described in {[}4{]} as the total percentage of problem
+domain elements identified compared to a benchmark. However, since we
+have no accesse to any requirement data, we will use the conclusions of
+{[}4{]} to compare the different scenarios of tacit knowledge (known
+unknowns, unknown knowns and unknowns unknowns).
 
-\hypertarget{using-argumentation-to-explain-ambiguity-in-requirements-elicitation-interviews}{%
-\section{Using Argumentation to Explain Ambiguity in Requirements
-Elicitation
-Interviews}\label{using-argumentation-to-explain-ambiguity-in-requirements-elicitation-interviews}}
+The works presented in {[}4{]} concludes that: (1)analyst's domain
+knowledge(ADK) has small but statisticall significant effect on the
+effectiveness, (2)stakeholders' domain knowledge(SDK) has a big positive
+and significant influence and (3)analyst's interviewing skill and
+general training in requirement activities have also a big positive and
+significant influence. In this paper, we will focus only in comparing
+based on the domain knowledge holder since that knowledge can be
+measured.
 
-One of the major causes of ambiguities in elicitation interviews is the
-presence of tacit knowledge. In some cases ambiguities can't be always
-be explained as separated term, sometimes it is required to have a
-context. Even under these circumstances, the analyst must be able to
-identify and alleviate them in order to elicit relevant information of
-the system. For this purpose it is necessary to provide the analyst with
-proper tools. In this paper Yehia Elrakaiby et al. {[}3{]} proposed a
-theoretical framework to overcome ambiguity during interviews in the
-elicitation phase. The framework is based on the ``Argumentation
-theory''.
+\begin{longtable}[]{@{}lcc@{}}
+\caption{Influence of domain knowledge in the different tacit knowledge
+scenarios}\tabularnewline
+\toprule
+scenario & ADK & SDK\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+scenario & ADK & SDK\tabularnewline
+\midrule
+\endhead
+known unknowns & \(+\) & 0\tabularnewline
+unknown knowns & 0 & \(++\)\tabularnewline
+unknown unknowns & 0 & 0\tabularnewline
+\bottomrule
+\end{longtable}
 
-In that sense, Elrakaiby et al.~focus on one type of ambiguities, the
-``acceptance unclarity''. An acceptance unclarity occurs every time the
-analyst is able to assign an interpretation or meaning to the speech
-fragment of the stakeholder, the interpretation matches the intended
-meaning of the stakeholder, but the interpretation is not acceptable or
-justified. It could be either because it seems to be inaccurate to
-comprehend the problem, or analysts identify inconsistencies with their
-current understanding of the problem or domain knowledge. By using
-argumentation theory framework, statements and ambiguities can be
-characterized as ``arguments'' and ``attacks'' respectively.
+We can observed in Table 1 that it is more likely to be effective in the
+scenario of \emph{unknown knowns} because the stakeholders' domain
+knowledge have more influence than analyst's domain knowledge. On the
+other hand, the analyst's interviewing skills will have different
+approaches in the case of \emph{known unknowns} and \emph{unknown
+knowns}. In the first case, the interview will be more focused on
+challenging assumptions and implications, and in the latter case on
+spoting glympses of stakeholders' hidden knowledge.
 
-Argumentation theory models a type of human dialog based on arguments
-and conclusions. It makes explicit attacks between arguments and the
-argumentation flow that leads to conclusions. A basic model in this
-framework is a pair \((A,D)\), where \(A\) is a set of arguments and
-\(D\) is a set of attacks among those arguments. For example, a set
-\(A\) is defined as \(A = \{A1,A2,A3\}\), and a possible set of attacks
-could be \(D = \{(A1,A3)\}\). Which means that if A1 is realizable then
-A3 can't be realizable.
+\hypertarget{papers-summary}{%
+\section{Papers summary}\label{papers-summary}}
 
-In the paper, Elrakaiby et al.~models statements given by the
-stakeholders, analysts domain knowledge and analysts inferences as
-arguments, and ambiguities between them as attacks. For example, let say
-the analyst listens the following statement \emph{the professor will
-upload the task description within three days} (A1), but the analyst
-know (domain knowledge) that \emph{the professor may be on a business
-meeting} (A2), so the analyst think (inference) that \emph{it may be
-possible that it will be take longer to upload the task description}
-(A3). In this scenario the set of attacks \(D\) is given by
-\(D = \{(A1,A3)\}\). Thus, since there is an attack it is possible to
-ask for clarifications or details.
-
-The theoretical framework proposed by Elrakaiby et al.~allows analysts
-to detect and minimize ambiguities during elicitation interviews, while
-most of the methods that focus on ambiguities analyze written texts. On
-the other hand, this framework focuses in more complex ambiguities that
-cannot be view as single terms.
-
-\hypertarget{effect-of-domain-knowledge-on-elicitation-effectiveness-an-internally-replicated-controlled-experiment}{%
-\section{Effect of Domain Knowledge on Elicitation Effectiveness: An
-Internally Replicated Controlled
-Experiment}\label{effect-of-domain-knowledge-on-elicitation-effectiveness-an-internally-replicated-controlled-experiment}}
-
-The effectiveness of elicitation interviews may be influenced by analyst
-skills or characteristics. In these high intensive oral communication
-scenario the analyst must be able to draw out relevant information and
-needs from the stakeholders. It has been reported that the effectiveness
-of the interviews has a direct relation with the domain knowledge of the
-analyst. However, there are also studies suggesting that in some cases
-the domain knowledge have negatives effects in the effectiveness of
-interviews.
-
-In this paper {[}4{]}, Aranda et al.~studied the influence of the
-analyst domain knowledge on the effectiveness of elicitation interviews.
-The main question they tried to answer was
-
-\emph{Does analyst domain knowledge influence (either positively or
-negatively) the effectiveness of the requirements elicitation activity?}
-
-For this purpose, the authors performed the study in two stages. They
-performed an initial baseline experiment with two domain problems, and
-then they performed an internal replication with two other domain
-problems. Furthermore, the authors divided the elicitation process in
-two phases. The elicitation phase which is the actual interview with the
-stakeholder, and the reporting phase in which the analyst understands
-and documents the information gathered in the elicitation phase.
-
-One remark of the study is that the authors chose students because of
-their lack of experience in elicitation interviews, isolation of the
-domain knowledge, and to analyze, in the internal replication, the
-influence of the training in requirements engineering in elicitation
-interviews. In the study participated post-graduated students as
-interviewers and two professors as interviewees. The students should
-make open interviews and elicit the information afterwards. Moreover,
-for each domain problem the students were separated in two groups based
-on their level of domain knowledge, \emph{domain-aware} and
-\emph{domain-ignorant}. On the other hand, the effectiveness of the
-elicitation's was based on the comparison between the number of
-concepts, processes and requirements elicited by the students and the
-benchmarks.
-
-The results of the baseline experiment suggest that the domain knowledge
-of the analysts has no significant influence in the effectiveness of the
-elicitation interviews. However, the results also suggest that the
-domain knowledge of the interviewees has statistically significant
-influence. Supplementary, the results of the internal replication also
-suggest that the domain knowledge of the stakeholders is more relevant
-than the analysts', in term of effectiveness of the elicitation
-interviews. Nevertheless, these results also show that the positive
-effects of the training in requirements engineering of the interviewers,
-with these effects being as relevant as interviewees' domain knowledge.
-
-\hypertarget{requirements-elicitation-towards-the-unknown-unknowns}{%
-\section{Requirements elicitation: Towards the Unknown
-Unknowns}\label{requirements-elicitation-towards-the-unknown-unknowns}}
+\hypertarget{requirements-elicitation-towards-the-unknown-unknowns-sutcliffe2013requirements}{%
+\subsection{Requirements elicitation: Towards the Unknown Unknowns
+{[}2{]}}\label{requirements-elicitation-towards-the-unknown-unknowns-sutcliffe2013requirements}}
 
@@
 
+\hypertarget{using-argumentation-to-explain-ambiguity-in-requirements-elicitation-interviews-elrakaiby2017using}{%
+\subsection{Using Argumentation to Explain Ambiguity in Requirements
+Elicitation Interviews
+{[}3{]}}\label{using-argumentation-to-explain-ambiguity-in-requirements-elicitation-interviews-elrakaiby2017using}}
+
+One of the major causes of ambiguities in elicitation interviews is the
+presence of tacit knowledge. In some cases ambiguities can't be always
+be explained as separated term, sometimes it is required to have a
+context. Even under these circumstances, the analyst must be able to
+identify and alleviate them in order to elicit relevant information of
+the system. For this purpose it is necessary to provide the analyst with
+proper tools. In this paper Yehia Elrakaiby et al.~proposed a
+theoretical framework to overcome ambiguity during interviews in the
+elicitation phase. The framework is based on the ``Argumentation
+theory''.
+
+In that sense, Elrakaiby et al.~focus on one type of ambiguities, the
+``acceptance unclarity''. An acceptance unclarity occurs every time the
+analyst is able to assign an interpretation or meaning to the speech
+fragment of the stakeholder, the interpretation matches the intended
+meaning of the stakeholder, but the interpretation is not acceptable or
+justified. It could be either because it seems to be inaccurate to
+comprehend the problem, or analysts identify inconsistencies with their
+current understanding of the problem or domain knowledge. By using
+argumentation theory framework, statements and ambiguities can be
+characterized as ``arguments'' and ``attacks'' respectively.
+
+Argumentation theory models a type of human dialog based on arguments
+and conclusions. It makes explicit attacks between arguments and the
+argumentation flow that leads to conclusions. A basic model in this
+framework is a pair \((A,D)\), where \(A\) is a set of arguments and
+\(D\) is a set of attacks among those arguments. For example, a set
+\(A\) is defined as \(A = \{A1,A2,A3\}\), and a possible set of attacks
+could be \(D = \{(A1,A3)\}\). Which means that if A1 is realizable then
+A3 can't be realizable.
+
+In the paper, Elrakaiby et al.~models statements given by the
+stakeholders, analysts domain knowledge and analysts inferences as
+arguments, and ambiguities between them as attacks. For example, let say
+the analyst listens the following statement \emph{the professor will
+upload the task description within three days} (A1), but the analyst
+know (domain knowledge) that \emph{the professor may be on a business
+meeting} (A2), so the analyst think (inference) that \emph{it may be
+possible that it will be take longer to upload the task description}
+(A3). In this scenario the set of attacks \(D\) is given by
+\(D = \{(A1,A3)\}\). Thus, since there is an attack it is possible to
+ask for clarifications or details.
+
+The theoretical framework proposed by Elrakaiby et al.~allows analysts
+to detect and minimize ambiguities during elicitation interviews, while
+most of the methods that focus on ambiguities analyze written texts. On
+the other hand, this framework focuses in more complex ambiguities that
+cannot be view as single terms.
+
+\hypertarget{effect-of-domain-knowledge-on-elicitation-effectiveness-an-internally-replicated-controlled-experiment-aranda2016effect}{%
+\subsection{Effect of Domain Knowledge on Elicitation Effectiveness: An
+Internally Replicated Controlled Experiment
+{[}4{]}}\label{effect-of-domain-knowledge-on-elicitation-effectiveness-an-internally-replicated-controlled-experiment-aranda2016effect}}
+
+The effectiveness of elicitation interviews may be influenced by analyst
+skills or characteristics. In these high intensive oral communication
+scenario the analyst must be able to draw out relevant information and
+needs from the stakeholders. It has been reported that the effectiveness
+of the interviews has a direct relation with the domain knowledge of the
+analyst. However, there are also studies suggesting that in some cases
+the domain knowledge have negatives effects in the effectiveness of
+interviews.
+
+In this paper Aranda et al.~studied the influence of the analyst domain
+knowledge on the effectiveness of elicitation interviews. The main
+question they tried to answer was
+
+\begin{quote}
+\emph{Does analyst domain knowledge influence (either positively or
+negatively) the effectiveness of the requirements elicitation activity?}
+\end{quote}
+
+For this purpose, the authors performed the study in two stages. They
+performed an initial baseline experiment with two domain problems, and
+then they performed an internal replication with two other domain
+problems. Furthermore, the authors divided the elicitation process in
+two phases. The elicitation phase which is the actual interview with the
+stakeholder, and the reporting phase in which the analyst understands
+and documents the information gathered in the elicitation phase.
+
+One remark of the study is that the authors chose students because of
+their lack of experience in elicitation interviews, isolation of the
+domain knowledge, and to analyze, in the internal replication, the
+influence of the training in requirements engineering in elicitation
+interviews. In the study participated post-graduated students as
+interviewers and two professors as interviewees. The students should
+make open interviews and elicit the information afterwards. Moreover,
+for each domain problem the students were separated in two groups based
+on their level of domain knowledge, \emph{domain-aware} and
+\emph{domain-ignorant}. On the other hand, the effectiveness of the
+elicitation's was based on the comparison between the number of
+concepts, processes and requirements elicited by the students and the
+benchmarks.
+
+The results of the baseline experiment suggest that the domain knowledge
+of the analysts has no significant influence in the effectiveness of the
+elicitation interviews. However, the results also suggest that the
+domain knowledge of the interviewees has statistically significant
+influence. Supplementary, the results of the internal replication also
+suggest that the domain knowledge of the stakeholders is more relevant
+than the analysts', in term of effectiveness of the elicitation
+interviews. Nevertheless, these results also show that the positive
+effects of the training in requirements engineering of the interviewers,
+with these effects being as relevant as interviewees' domain knowledge.
+
 \hypertarget{conclusions}{%

### 2018-01-07 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

@@
 \begin{abstract}
-I need an abstract
+Interviews are the most common technique in requirements elicitation.
+However, the presence of tacit knowledge have an important influence on
+interviews success. In this paper, we describe a tacit knowledge
+classification. Then we make use of a theoretical framework and examples
+to detect and minimize the effects of tacit knowledge. Finally, we
+analyze how likely is to have a sucessful elicitation interviews based
+on the tacit knowledge classification.
 
 % lncs keyword extension 
-\keywords{I, need, keywords}
+\keywords{interview, tacit knowledge, elicitation}
 
@@
 
-I need an introduction\ldots{}
+Requirements engineering is the subset of systems engineering concerned
+with discovering, developing, tracing, analyzing, qualifying,
+communicating and managing requirements that define the system at
+succesive levels of abstraction {[}1{]}. The first step of requirements
+engineering is requirements elicitation which is defined as the process
+of finding and formulation requirements {[}2{]}, and this process has
+many barriers due to stakeholders are not able to express their needs,
+explain what they do and why, conflicting demands, or new demands once
+other are met, just to mention some examples.
 
-\hypertarget{my-approach-i-need-a-section-title}{%
-\section{My approach (i need a section
-title)}\label{my-approach-i-need-a-section-title}}
+One of the most used techiques to elict requirements is open interviews,
+and also is considered the most effective way to transfer domain
+knowledge {[}3{]}. However, the success of interviews depends on mainly
+two factors, analyst set of interviewing skills and stakeholders domain
+knowledge; nonetheless, statistically analyst domain knowledge is
+important but not as relevant as the other two{[}4{]}. Therefore,
+analyst should make use of tools and techniques to detect and elicit
+tacit knowledge form stakeholders. Tacit knowledge is in requirements
+engineering is defined as the knowledge that a stakeholders has, but
+does not pass to the requirements analyst {[}5{]}.
 
-\hypertarget{tacit-knowledge-in-elicitation-interviews}{%
-\subsection{Tacit knowledge in elicitation
-interviews}\label{tacit-knowledge-in-elicitation-interviews}}
+In this paper we describe a classification of tacit knowledge in
+elicitation interviews based on {[}6{]}. Then we apply the theoretical
+framework described in {[}3{]} in examples to show how to deal with
+tacit knowledge. The examples were selected in order to match the each
+scenario of the classification. Finally, we use the result from {[}4{]}
+to identify in which scenario is most likely to perform a succesful
+interview.
 
-Requirements elicitation is the process of finding and formulation
-requirements, and this process has many barriers due to stakeholders are
-not able to express their needs, explain what they do and why,
-conflicting demands, or new demands once other are met{[}1{]}, just to
-mention some examples. Many analyst consider interviews the most
-important elicitation technique, and usually elicitation process starts
-with interviewing the stakeholders. Interviews allow analysts to check
-their understanding about the problem domain immediately and ask for
-clarifications. Moreover, this technique is versatile in the sense of it
-is possible that new and unexpected issues come up and they can be
-attacked at that moment.
+The remainder paper is structured as follows. In section 2 we provide a
+summary of the papers used to write this paper. In section 3 we present
+our approach. Finally, in section 4, we present our conclusions.
 
-However, elicit tacit knowledge in interviews is still a hard task to
-do. This tacit knowledge can be classified in four groups as describe in
-{[}2{]}. The \textbf{known knowns}, \textbf{known unknowns},
-\textbf{unknown knowns} and \textbf{unknown unknowns}. The known knowns
-is the knowledge that is documented, expressible, and relevant to the
-system. In order words, is the scenario in which it is possible to
-elicit since the beginning all the requirements, there is no tacit
-knowledge. The known unknowns is the knowledge that cannot be
-expressible because the stakeholders are not aware of their lack of
-domain knowledge, their might forget it. In this case analyst are aware
-of the domain knowledge and therefore, their job is to challenge
-assumptions or implications. The unknown knowns is the knowledge that
-stakeholders hold but it is not documented by some reason. Thus,
-analysts should use their interviewing skill to elicit when they spot
-any glimpse of that knowledge. The unknown unknowns is the knowledge
-that neither the analysts nor stakeholders are aware.
-
-\hypertarget{challenge-tacit-knowledge}{%
-\subsection{Challenge tacit knowledge}\label{challenge-tacit-knowledge}}
-
-The unknowness clarification presented in above suggest the presence of
-three problems. The goal is to go from any scenario in which tacit
-knowledge exists to known knowns. In order to achieve that goal and take
-the advantages presented in elicitation interviews (immediately
-clarification of assumptions and debate of implications) we are going to
-use the theoretical framework described by Elrakaiby {[}3{]}. In this
-framework we model the interview as a set of arguments and attacks
-between them. In that sense, we will able to spot ambiguities and tacit
-knowledge in terms of inconsistencies and insufficiency of information.
-We will adapt some examples from {[}3{]} to show how each tacit
-knowledge scenario can be addresed.
-
-\textbf{known unknowns}: In the following example the domain knowledge
-of the analyst is used to detect inconsistencies (attacks), because the
-stakeholder didn't take into account relevant information about domain
-application (location of trash bins).
-
-A customers wanted a recycling-support system and one of the goals was
-\emph{to avoid fines from the municipality for incorrect recycling}.
-According to the domain knowledge of the analyst, \emph{trash bins are
-placed along the streets}. Thus, the goal was inconsistent with the
-domain knowledge of the analyst because \emph{there is no way to trace
-back person who brakes the recycling rule}. This scenario can be modeled
-using arguments and attacks as follows:
-
-The arguments: (A1)trash bins are placed along the streets, (A2)since
-trash bins are placed along the streets, the trash owner cannot be
-traced back. (B1)people who do not recycle should be fined (B2)to fine
-people, the municipality must be able to trace products in trash bins
-back to their owners.
-
-Attacks: A2 attacks B1, and viceversa.
-
-\textbf{unknown knowns}: In the following example analyst challenges the
-stakeholder statement, as a result the stakeholder reveals new
-information (reply).
-
-A customers wants to develop a system to allow patients to measure the
-amount of glucose in their blood, and then send the result to their
-general practitioner. If the glucose level is above a certain threshold,
-the practitioner pays a visit to the patient. The customer said:
-\emph{in one-two days the doctor sees the notification in the system}.
-Then analyst asked: \emph{What happens if the doctor is not available
-for any reason?}. The customer replied: \emph{The general practitioner
-is substituted by another doctor who accesses the same system}.
-
-The arguments: (A1)in one-two days the doctor sees the
-notification,(B1)the doctor might be unavailable,(B2)since the the
-doctor might be unavailable, the notification might be delayed.
-
-The attacks: A1 attacks B2, and viceversa
-
-\textbf{unknown unknowns}: In the following example the stakeholder
-didn't notice the inconsistency between his statements, but the analyst
-did and asked for clarification. However, the stakeholder couldn't give
-an answers due to his ignorance.
-
-One of the customers wants to develop an app to manage medical-related
-reservation in Tuscani. The costumer mentioned that the \emph{current
-reservation system, based on phone calls, was centralised}. During the
-interview, the customer said that \emph{depending on where the
-examination/visit will be, the patient has to call Nottola or Siena}.
-The analyst could not understand how this realization was possible since
-it means the reservation system is not centralized. Therefore the
-analyst asked for clarification and the stakeholder couldn't give any
-acceptable answer.
-
-The arguments: (A1)the current reservation is centralized, (B1)depending
-on where the examination/visit will be (B2)the patience has to call
-Nottola or Siena, (B3) since it is possible to call either Nottola or
-Siena the system is not centralized.
-
-The attacks: A1 attacks B3, and viceversa
-
-\hypertarget{limits-of-elicited-knowledge}{%
-\subsection{Limits of elicited
-knowledge}\label{limits-of-elicited-knowledge}}
-
-In the last section we present how to use a theoretical framework based
-on arguments and attacks to addresed the different levels of tacit
-knowledge. In this section we will compare in which scenario of tacit
-knowledge the elicitation interview is more effective based on Aranda et
-al.~work {[}4{]} about the effect of domain knowledge on elicitation
-process.\\
-Effectiveness is described in {[}4{]} as the total percentage of problem
-domain elements identified compared to a benchmark. However, since we
-have no accesse to any requirement data, we will use the conclusions of
-{[}4{]} to compare the different scenarios of tacit knowledge (known
-unknowns, unknown knowns and unknowns unknowns).
-
-The works presented in {[}4{]} concludes that: (1)analyst's domain
-knowledge(ADK) has small but statisticall significant effect on the
-effectiveness, (2)stakeholders' domain knowledge(SDK) has a big positive
-and significant influence and (3)analyst's interviewing skill and
-general training in requirement activities have also a big positive and
-significant influence. In this paper, we will focus only in comparing
-based on the domain knowledge holder since that knowledge can be
-measured.
-
-\begin{longtable}[]{@{}lcc@{}}
-\caption{Influence of domain knowledge in the different tacit knowledge
-scenarios}\tabularnewline
-\toprule
-scenario & ADK & SDK\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-scenario & ADK & SDK\tabularnewline
-\midrule
-\endhead
-known unknowns & \(+\) & 0\tabularnewline
-unknown knowns & 0 & \(++\)\tabularnewline
-unknown unknowns & 0 & 0\tabularnewline
-\bottomrule
-\end{longtable}
-
-We can observed in Table 1 that it is more likely to be effective in the
-scenario of \emph{unknown knowns} because the stakeholders' domain
-knowledge have more influence than analyst's domain knowledge. On the
-other hand, the analyst's interviewing skills will have different
-approaches in the case of \emph{known unknowns} and \emph{unknown
-knowns}. In the first case, the interview will be more focused on
-challenging assumptions and implications, and in the latter case on
-spoting glympses of stakeholders' hidden knowledge.
-
-\hypertarget{papers-summary}{%
-\section{Papers summary}\label{papers-summary}}
+\hypertarget{background}{%
+\section{Background}\label{background}}
 
@@
 \subsection{Requirements elicitation: Towards the Unknown Unknowns
-{[}2{]}}\label{requirements-elicitation-towards-the-unknown-unknowns-sutcliffe2013requirements}}
+{[}6{]}}\label{requirements-elicitation-towards-the-unknown-unknowns-sutcliffe2013requirements}}
 
@@
 
+\hypertarget{tacit-knowledge-in-elicitation-interviews}{%
+\section{Tacit knowledge in elicitation
+interviews}\label{tacit-knowledge-in-elicitation-interviews}}
+
+\hypertarget{types-of-tacit-knowledge}{%
+\subsection{Types of tacit knowledge}\label{types-of-tacit-knowledge}}
+
+Many analyst consider interviews the most important elicitation
+technique, and usually elicitation process starts with interviewing the
+stakeholders. Interviews allow analysts to check their understanding
+about the problem domain immediately and ask for clarifications.
+Moreover, this technique is versatile in the sense of it is possible
+that new and unexpected issues come up and they can be attacked at that
+moment.
+
+However, elicit tacit knowledge in interviews is still a hard task to
+do. This tacit knowledge can be classified in four groups as describe in
+{[}6{]}. The \textbf{known knowns}, \textbf{known unknowns},
+\textbf{unknown knowns} and \textbf{unknown unknowns}. The known knowns
+is the knowledge that is documented, expressible, and relevant to the
+system. In order words, is the scenario in which it is possible to
+elicit since the beginning all the requirements, there is no tacit
+knowledge. The known unknowns is the knowledge that cannot be
+expressible because the stakeholders are not aware of their lack of
+domain knowledge, their might forget it. In this case analyst are aware
+of the domain knowledge and therefore, their job is to challenge
+assumptions or implications. The unknown knowns is the knowledge that
+stakeholders hold but it is not documented by some reason. Thus,
+analysts should use their interviewing skill to elicit when they spot
+any glimpse of that knowledge. The unknown unknowns is the knowledge
+that neither the analysts nor stakeholders are aware.
+
+\hypertarget{how-to-deal-with-tacit-knowledge}{%
+\subsection{How to deal with tacit
+knowledge}\label{how-to-deal-with-tacit-knowledge}}
+
+The unknowness clarification presented in above suggest the presence of
+three problems. The goal is to go from any scenario in which tacit
+knowledge exists to known knowns. In order to achieve that goal and take
+the advantages presented in elicitation interviews (immediately
+clarification of assumptions and debate of implications) we are going to
+use the theoretical framework described by Elrakaiby {[}3{]}. In this
+framework we model the interview as a set of arguments and attacks
+between them. In that sense, we will able to spot ambiguities and tacit
+knowledge in terms of inconsistencies and insufficiency of information.
+We will adapt some examples from {[}3{]} to show how each tacit
+knowledge scenario can be addresed.
+
+\textbf{known unknowns}: In the following example the domain knowledge
+of the analyst is used to detect inconsistencies (attacks), because the
+stakeholder didn't take into account relevant information about domain
+application (location of trash bins).
+
+A customers wanted a recycling-support system and one of the goals was
+\emph{to avoid fines from the municipality for incorrect recycling}.
+According to the domain knowledge of the analyst, \emph{trash bins are
+placed along the streets}. Thus, the goal was inconsistent with the
+domain knowledge of the analyst because \emph{there is no way to trace
+back person who brakes the recycling rule}. This scenario can be modeled
+using arguments and attacks as follows:
+
+The arguments: (A1)trash bins are placed along the streets, (A2)since
+trash bins are placed along the streets, the trash owner cannot be
+traced back. (B1)people who do not recycle should be fined (B2)to fine
+people, the municipality must be able to trace products in trash bins
+back to their owners.
+
+Attacks: A2 attacks B1, and viceversa.
+
+\textbf{unknown knowns}: In the following example analyst challenges the
+stakeholder statement, as a result the stakeholder reveals new
+information (reply).
+
+A customers wants to develop a system to allow patients to measure the
+amount of glucose in their blood, and then send the result to their
+general practitioner. If the glucose level is above a certain threshold,
+the practitioner pays a visit to the patient. The customer said:
+\emph{in one-two days the doctor sees the notification in the system}.
+Then analyst asked: \emph{What happens if the doctor is not available
+for any reason?}. The customer replied: \emph{The general practitioner
+is substituted by another doctor who accesses the same system}.
+
+The arguments: (A1)in one-two days the doctor sees the
+notification,(B1)the doctor might be unavailable,(B2)since the the
+doctor might be unavailable, the notification might be delayed.
+
+The attacks: A1 attacks B2, and viceversa
+
+\textbf{unknown unknowns}: In the following example the stakeholder
+didn't notice the inconsistency between his statements, but the analyst
+did and asked for clarification. However, the stakeholder couldn't give
+an answers due to his ignorance.
+
+One of the customers wants to develop an app to manage medical-related
+reservation in Tuscani. The costumer mentioned that the \emph{current
+reservation system, based on phone calls, was centralised}. During the
+interview, the customer said that \emph{depending on where the
+examination/visit will be, the patient has to call Nottola or Siena}.
+The analyst could not understand how this realization was possible since
+it means the reservation system is not centralized. Therefore the
+analyst asked for clarification and the stakeholder couldn't give any
+acceptable answer.
+
+The arguments: (A1)the current reservation is centralized, (B1)depending
+on where the examination/visit will be (B2)the patience has to call
+Nottola or Siena, (B3) since it is possible to call either Nottola or
+Siena the system is not centralized.
+
+The attacks: A1 attacks B3, and viceversa
+
+\hypertarget{limits-of-elicited-knowledge}{%
+\subsection{Limits of elicited
+knowledge}\label{limits-of-elicited-knowledge}}
+
+In the last section we present how to use a theoretical framework based
+on arguments and attacks to addresed the different levels of tacit
+knowledge. In this section we will compare in which scenario of tacit
+knowledge the elicitation interview would be more effective based on
+Aranda et al.~work {[}4{]} about the effect of domain knowledge on
+elicitation process.\\
+Effectiveness is described in {[}4{]} as the total percentage of problem
+domain elements identified compared to a benchmark. However, since we
+have no accesse to any requirement data, we will use the conclusions of
+{[}4{]} to compare the different scenarios of tacit knowledge (known
+unknowns, unknown knowns and unknowns unknowns).
+
+The works presented in {[}4{]} concludes that: (1)analyst's domain
+knowledge(ADK) has small but statisticall significant effect on the
+effectiveness, (2)stakeholders' domain knowledge(SDK) has a big positive
+and significant influence and (3)analyst's interviewing skill and
+general training in requirement activities have also a big positive and
+significant influence. In this paper, we will focus only in comparing
+based on the domain knowledge holder since that knowledge can be
+measured.
+
+\begin{longtable}[]{@{}lcc@{}}
+\caption{Influence of domain knowledge in the different tacit knowledge
+scenarios}\tabularnewline
+\toprule
+scenario & ADK & SDK\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+scenario & ADK & SDK\tabularnewline
+\midrule
+\endhead
+known unknowns & \(+\) & 0\tabularnewline
+unknown knowns & 0 & \(++\)\tabularnewline
+unknown unknowns & 0 & 0\tabularnewline
+\bottomrule
+\end{longtable}
+
+We can observed in Table 1 that it is more likely to be effective in the
+scenario of \emph{unknown knowns} because the stakeholders' domain
+knowledge have more influence than analyst's domain knowledge. On the
+other hand, the analyst's interviewing skills will have different
+approaches in the case of \emph{known unknowns} and \emph{unknown
+knowns}. In the first case, the interview will be more focused on
+challenging assumptions and implications, and in the latter case on
+spoting glympses of stakeholders' hidden knowledge.
+
 \hypertarget{conclusions}{%
@@
 
-I need some conclusions
-
-\hypertarget{what-ill-do}{%
-\section{What i'll do}\label{what-ill-do}}
-
-Explain tacit knowledge explain domain knowledge Explain acceptance
-unclarity Explain Dung's framework Explain ASPIC+ Inconsistencies It's
-highly influenced by the domain knowledge of the analyst
-
-\newpage
+Elicitation interviews is not an easy task. Like in any intensive oral
+communication there are missunderstandings related to tacit knowledge.
+In our work we focus on analysing the different levels of how tacit
+knowledge{[}6{]} would affect the effectiveness of elicitation
+interviews. Moreover, we use the theoretical framework described in
+{[}3{]} to indentify and manage tacit knowledge during interviews. And
+finally, we analyze based on the results of {[}4{]} in which scenario of
+tacit knowledge it is more likely to have a sucessful elictation
+interview.
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-dick2017requirements}{}%
+{[}1{]} J. Dick, E. Hull, and K. Jackson, \emph{Requirements
+engineering}. Springer International Publishing, 2017.
+
 \leavevmode\hypertarget{ref-lauesen2001softwarereq}{}%
-{[}1{]} S. Lauesen, \emph{Software requirements: Styles and techniques},
+{[}2{]} S. Lauesen, \emph{Software requirements: Styles and techniques},
 1st ed. Pearson Education, 2001.
-
-\leavevmode\hypertarget{ref-sutcliffe2013requirements}{}%
-{[}2{]} A. Sutcliffe and P. Sawyer, ``Requirements elicitation: Towards
-the unknown unknowns,'' in \emph{Requirements engineering conference
-(re), 2013 21st ieee international}, 2013, pp. 92--104.
 
@@
 
+\leavevmode\hypertarget{ref-ferrari2015ambiguity}{}%
+{[}5{]} A. Ferrari, P. Spoletini, and S. Gnesi, ``Ambiguity as a
+resource to disclose tacit knowledge,'' in \emph{Requirements
+engineering conference (re), 2015 ieee 23rd international}, 2015, pp.
+26--35.
+
+\leavevmode\hypertarget{ref-sutcliffe2013requirements}{}%
+{[}6{]} A. Sutcliffe and P. Sawyer, ``Requirements elicitation: Towards
+the unknown unknowns,'' in \emph{Requirements engineering conference
+(re), 2013 21st ieee international}, 2013, pp. 92--104.
+
 \end{document}

### 2018-01-07 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

@@
 interviews success. In this paper, we describe a tacit knowledge
-classification. Then we make use of a theoretical framework and examples
-to detect and minimize the effects of tacit knowledge. Finally, we
-analyze how likely is to have a sucessful elicitation interviews based
-on the tacit knowledge classification.
+classification. Then, we make use, with examples, of a theoretical
+framework to detect and minimize the effects of tacit knowledge.
+Finally, we analyze how likely is to have a successful elicitation
+interviews based on the tacit knowledge classification.
 
@@
 communicating and managing requirements that define the system at
-succesive levels of abstraction {[}1{]}. The first step of requirements
+successive levels of abstraction {[}1{]}. The first step of requirements
 engineering is requirements elicitation which is defined as the process
@@
 
-One of the most used techiques to elict requirements is open interviews,
-and also is considered the most effective way to transfer domain
-knowledge {[}3{]}. However, the success of interviews depends on mainly
-two factors, analyst set of interviewing skills and stakeholders domain
-knowledge; nonetheless, statistically analyst domain knowledge is
+One of the most used techniques to elicit requirements is open
+interviews, and also is considered the most effective way to transfer
+domain knowledge {[}3{]}. However, the success of interviews depends on
+mainly two factors, analyst set of interviewing skills and stakeholders
+domain knowledge; nonetheless, statistically analyst domain knowledge is
 important but not as relevant as the other two{[}4{]}. Therefore,
@@
 scenario of the classification. Finally, we use the result from {[}4{]}
-to identify in which scenario is most likely to perform a succesful
+to identify in which scenario is most likely to perform a successful
 interview.
@@
 
-Attacks: A2 attacks B1, and viceversa.
+Attacks: A2 attacks B1, and vice versa.
 
@@
 
-The attacks: A1 attacks B2, and viceversa
+The attacks: A1 attacks B2, and vice versa
 
@@
 reservation in Tuscani. The costumer mentioned that the \emph{current
-reservation system, based on phone calls, was centralised}. During the
+reservation system, based on phone calls, was centralized}. During the
 interview, the customer said that \emph{depending on where the
@@
 
-The attacks: A1 attacks B3, and viceversa
+The attacks: A1 attacks B3, and vice versa
 
@@
 In the last section we present how to use a theoretical framework based
-on arguments and attacks to addresed the different levels of tacit
+on arguments and attacks to addressed the different levels of tacit
 knowledge. In this section we will compare in which scenario of tacit
@@
 domain elements identified compared to a benchmark. However, since we
-have no accesse to any requirement data, we will use the conclusions of
+have no access to any requirement data, we will use the conclusions of
 {[}4{]} to compare the different scenarios of tacit knowledge (known
@@
 The works presented in {[}4{]} concludes that: (1)analyst's domain
-knowledge(ADK) has small but statisticall significant effect on the
+knowledge(ADK) has small but statistically significant effect on the
 effectiveness, (2)stakeholders' domain knowledge(SDK) has a big positive
@@
 challenging assumptions and implications, and in the latter case on
-spoting glympses of stakeholders' hidden knowledge.
+spotting glimpses of stakeholders' hidden knowledge.
 
@@
 Elicitation interviews is not an easy task. Like in any intensive oral
-communication there are missunderstandings related to tacit knowledge.
-In our work we focus on analysing the different levels of how tacit
+communication there are misunderstandings related to tacit knowledge. In
+our work we focus on analyzing the different levels of how tacit
 knowledge{[}6{]} would affect the effectiveness of elicitation
 interviews. Moreover, we use the theoretical framework described in
-{[}3{]} to indentify and manage tacit knowledge during interviews. And
+{[}3{]} to identify and manage tacit knowledge during interviews. And
 finally, we analyze based on the results of {[}4{]} in which scenario of
-tacit knowledge it is more likely to have a sucessful elictation
+tacit knowledge it is more likely to have a successful elicitation
 interview.

### 2018-01-07 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

@@
             pdfauthor={Daniel Paredes},
-            pdftitle={I need a title},
+            pdftitle={Influence of tacit knowledge in elicitation interviews},
             colorlinks=true,
@@
 
-\title{I need a title}
+\title{Influence of tacit knowledge in elicitation interviews}
 \author{Daniel Paredes}
@@
 important but not as relevant as the other two{[}4{]}. Therefore,
-analyst should make use of tools and techniques to detect and elicit
-tacit knowledge form stakeholders. Tacit knowledge is in requirements
+analyst depends on the use of tools and techniques to detect and elicit
+tacit knowledge form stakeholders. Tacit knowledge in requirements
 engineering is defined as the knowledge that a stakeholders has, but
@@
 elicitation interviews based on {[}6{]}. Then we apply the theoretical
-framework described in {[}3{]} in examples to show how to deal with
-tacit knowledge. The examples were selected in order to match the each
+framework described in {[}3{]} to examples to show how to deal with
+tacit knowledge. The examples were selected in order to analyze each
 scenario of the classification. Finally, we use the result from {[}4{]}
@@
 
-This levels of knowledge implies problems of different perspective of
-the elicitation process that involves analysts and stakeholders. The
-\emph{known knowns} is a simple scenario since the counterparts are
-aware of the domain problem which is expressible and articulated. In the
-case of the \emph{known unknowns}, the analysts has a domain knowledge
-and they should be able draw out the information from the stakeholders
-that they might be unaware of. In contrast, in the \emph{unknown knowns}
-scenario the stakeholders are the ones that are aware of the domain
-knowledge but for some reason it is no articulated, and therefore, the
-analysts once they notice any glimpse of the stakeholders information
-they should able to discover and elicit that. On the other hand, in the
-case of \emph{unknown unknowns} both counterparts are unaware of the
-missing information that might be relevant to the system.
-
 Based on the perspectives described before, the authors identified three
@@
 Finally, the authors suggest four research directions to deal with the
-unknowness problem. Starting with the known unknown in which the analyst
-should challenging assumptions, implications, and relaxing domain
-constrains in order to increase the probability to elicit the unaware
-knowledge of the stakeholders. In the same direction, in the design
-discovery, which is a variant of the latter case, the analyst should
-deal with the the following statement ``I'll know what I want when I see
-it''. Thus, there is a need of prototyping or simulations as part of the
-elicitation process. In the case of the unknown knowns in which the
-analyst can elicit tacit knowledge by taking into account the background
-(political, cultural, emotional) of stakeholders, and use that
-background as an ``emotional guidance'' in order to draw out the
-relevant information. Finally, in the case of unknown unknowns the
-authors suggest to main approaches. The first one is based on the
-``over-the-horizon'' knowledge, in which authors proposed a
-socio-technical approach based on social media and e-communities. And
-the other one is using counter examples that can challenges the
-boundaries of the idea under development.
+unknowness problem. First, in \emph{known unknown} the analyst should
+challenging assumptions, implications, and relaxing domain constrains in
+order to increase the probability to elicit the unaware knowledge of the
+stakeholders. In the same direction, the design discovery, which is a
+variant of the latter case, the analyst should deal with the the
+following statement ``I'll know what I want when I see it''. Thus, there
+is a need of prototyping or simulations as part of the elicitation
+process. In the case of the \emph{unknown knowns} the analyst can elicit
+tacit knowledge by taking into account the background (political,
+cultural, emotional) of stakeholders, and use that background as an
+``emotional guidance'' in order to draw out the relevant information.
+Finally, in order to deal with \emph{unknown unknowns} the authors
+suggest two main approaches. The first one is based on the
+``over-the-horizon'' knowledge which is a socio-technical approach based
+on social media and e-communities. And the other one is using counter
+examples that can challenges the boundaries of the idea under
+development.
 
@@
 
-In that sense, Elrakaiby et al.~focus on one type of ambiguities, the
+In that sense, the authors focus on one type of ambiguities, the
 ``acceptance unclarity''. An acceptance unclarity occurs every time the
@@
 \(D\) is a set of attacks among those arguments. For example, a set
-\(A\) is defined as \(A = \{A1,A2,A3\}\), and a possible set of attacks
-could be \(D = \{(A1,A3)\}\). Which means that if A1 is realizable then
-A3 can't be realizable.
+\(A\) could be defined as \(A = \{A1,A2,A3\}\), and a possible set of
+attacks could be \(D = \{(A1,A3)\}\). Which means that if A1 is
+realizable then A3 can't be realizable.
 
-In the paper, Elrakaiby et al.~models statements given by the
-stakeholders, analysts domain knowledge and analysts inferences as
-arguments, and ambiguities between them as attacks. For example, let say
-the analyst listens the following statement \emph{the professor will
-upload the task description within three days} (A1), but the analyst
-know (domain knowledge) that \emph{the professor may be on a business
-meeting} (A2), so the analyst think (inference) that \emph{it may be
-possible that it will be take longer to upload the task description}
-(A3). In this scenario the set of attacks \(D\) is given by
-\(D = \{(A1,A3)\}\). Thus, since there is an attack it is possible to
-ask for clarifications or details.
+In the paper, statements given by the stakeholders, analysts domain
+knowledge and analysts inferences are modeled as arguments, and
+ambiguities between them as attacks. For example, let say the analyst
+listens the following statement \emph{the professor will upload the task
+description within three days} (A1), but the analyst know (domain
+knowledge) that \emph{the professor may be on a business meeting} (A2),
+so the analyst think (inference) that \emph{it may be possible that it
+will be take longer to upload the task description} (A3). In this
+scenario the set of attacks \(D\) is given by \(D = \{(A1,A3)\}\). Thus,
+since there is an attack it is possible to ask for clarifications.
 
-The theoretical framework proposed by Elrakaiby et al.~allows analysts
-to detect and minimize ambiguities during elicitation interviews, while
-most of the methods that focus on ambiguities analyze written texts. On
-the other hand, this framework focuses in more complex ambiguities that
-cannot be view as single terms.
+The theoretical framework proposed allows analysts to detect and
+minimize ambiguities during elicitation interviews, while most of the
+methods focus on ambiguities analysis in written texts. On the other
+hand, this framework focuses in more complex ambiguities that cannot be
+view as single terms.
 
@@
 The effectiveness of elicitation interviews may be influenced by analyst
-skills or characteristics. In these high intensive oral communication
+skills or characteristics. In this high intensive oral communication
 scenario the analyst must be able to draw out relevant information and
@@
 then they performed an internal replication with two other domain
-problems. Furthermore, the authors divided the elicitation process in
-two phases. The elicitation phase which is the actual interview with the
-stakeholder, and the reporting phase in which the analyst understands
-and documents the information gathered in the elicitation phase.
-
-One remark of the study is that the authors chose students because of
-their lack of experience in elicitation interviews, isolation of the
-domain knowledge, and to analyze, in the internal replication, the
-influence of the training in requirements engineering in elicitation
+problems. One remark of the study is that the authors chose students
+because of their lack of experience in elicitation interviews, isolation
+of the domain knowledge, and to analyze, in the internal replication,
+the influence of the training in requirements engineering in elicitation
 interviews. In the study participated post-graduated students as
@@
 suggest that the domain knowledge of the stakeholders is more relevant
-than the analysts', in term of effectiveness of the elicitation
-interviews. Nevertheless, these results also show that the positive
-effects of the training in requirements engineering of the interviewers,
-with these effects being as relevant as interviewees' domain knowledge.
+than the analysts', in terms of effectiveness of elicitation interviews.
+Nevertheless, these results also show that the positive effects of the
+training in requirements engineering of the interviewers, with these
+effects being as relevant as interviewees' domain knowledge.
 
@@
 of the domain knowledge and therefore, their job is to challenge
-assumptions or implications. The unknown knowns is the knowledge that
+assumptions or implications in order to elicit information that
+stakeholders are unaware of. The unknown knowns is the knowledge that
 stakeholders hold but it is not documented by some reason. Thus,
@@
 any glimpse of that knowledge. The unknown unknowns is the knowledge
-that neither the analysts nor stakeholders are aware.
+that neither the analysts nor stakeholders are aware but might be
+relevant to the project.
 
@@
 domain elements identified compared to a benchmark. However, since we
-have no access to any requirement data, we will use the conclusions of
+have no access to any requirement data, we will use the results from
 {[}4{]} to compare the different scenarios of tacit knowledge (known

### 2018-01-07 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

@@
 Interviews are the most common technique in requirements elicitation.
-However, the presence of tacit knowledge have an important influence on
-interviews success. In this paper, we describe a tacit knowledge
+However, the presence of tacit knowledge has an important influence on
+interview success. In this paper, we describe a tacit knowledge
 classification. Then, we make use, with examples, of a theoretical
 framework to detect and minimize the effects of tacit knowledge.
-Finally, we analyze how likely is to have a successful elicitation
-interviews based on the tacit knowledge classification.
+Finally, we analyze how likely it is to have a successful elicitation
+interview based on the tacit knowledge classification.
 
@@
 engineering is requirements elicitation which is defined as the process
-of finding and formulation requirements {[}2{]}, and this process has
-many barriers due to stakeholders are not able to express their needs,
-explain what they do and why, conflicting demands, or new demands once
-other are met, just to mention some examples.
+of finding and formulating requirements {[}2{]}, and this process has
+many barriers due to the fact that stakeholders are not able to express
+their needs, explain what they do and why, conflicting demands, or new
+demands once other are met, just to mention some examples.
 
 One of the most used techniques to elicit requirements is open
-interviews, and also is considered the most effective way to transfer
+interviews, and also it is considered the most effective way to transfer
 domain knowledge {[}3{]}. However, the success of interviews depends on
-mainly two factors, analyst set of interviewing skills and stakeholders
-domain knowledge; nonetheless, statistically analyst domain knowledge is
-important but not as relevant as the other two{[}4{]}. Therefore,
-analyst depends on the use of tools and techniques to detect and elicit
-tacit knowledge form stakeholders. Tacit knowledge in requirements
-engineering is defined as the knowledge that a stakeholders has, but
-does not pass to the requirements analyst {[}5{]}.
+mainly two factors, analyst's set of interviewing skills and
+stakeholders' domain knowledge; nonetheless, statistically analyst's
+domain knowledge is important but not as relevant as the other
+two{[}4{]}. Therefore, the analyst depends on the use of tools and
+techniques to detect and elicit tacit knowledge form stakeholders. Tacit
+knowledge in requirements engineering is defined as the knowledge that a
+stakeholders has, but does not pass to the requirements analyst {[}5{]}.
 
-In this paper we describe a classification of tacit knowledge in
+In this paper, we describe a classification of tacit knowledge in
 elicitation interviews based on {[}6{]}. Then we apply the theoretical
@@
 scenario of the classification. Finally, we use the result from {[}4{]}
-to identify in which scenario is most likely to perform a successful
-interview.
+to identify in which scenario a successful interview is most likely to
+occur.
 
-The remainder paper is structured as follows. In section 2 we provide a
-summary of the papers used to write this paper. In section 3 we present
-our approach. Finally, in section 4, we present our conclusions.
+The remainder of the paper is structured as follows. In section 2 we
+provide a summary of the papers used to write this paper. In section 3
+we present our approach. Finally, in section 4, we present our
+conclusions.
 
@@
 Elicitation in requirements engineering is still problematic because
-missing or mistaken requirements are hard to elicit, and this produce
-projects delays and have financial implications. In this paper, the
+missing or mistaken requirements are hard to elicit, and this produces
+projects delays and has financial implications. In this paper, the
 authors propose an elicitation review framework (ERF) in order to
@@
 Based on the perspectives described before, the authors identified three
-challenges to requirement elicitation. The first one is to identifying
-tacit knowledge (unknown knowns), even in the case the analyst presume
+challenges to requirement elicitation. The first one is to identify
+tacit knowledge (unknown knowns), even in the case the analyst presumes
 it exist (known unknowns). The second challenge is that the analyst
@@
 is the articulation of the knowledge. Thus, in the worst case scenario
-the goal is go from the unknown unknowns perspective to known knowns.
+the goal is to go from the unknown unknowns perspective to known knowns.
 
@@
 unknowness problem. First, in \emph{known unknown} the analyst should
-challenging assumptions, implications, and relaxing domain constrains in
-order to increase the probability to elicit the unaware knowledge of the
-stakeholders. In the same direction, the design discovery, which is a
-variant of the latter case, the analyst should deal with the the
-following statement ``I'll know what I want when I see it''. Thus, there
-is a need of prototyping or simulations as part of the elicitation
-process. In the case of the \emph{unknown knowns} the analyst can elicit
-tacit knowledge by taking into account the background (political,
+challenge assumptions, implications, and relax domain constrains in
+order to increase the probability of eliciting the unaware knowledge of
+the stakeholders. In the same direction, the \emph{design discovery},
+which is a variant of the latter case, the analyst should deal with the
+the following statement: ``I'll know what I want when I see it''. Thus,
+there is a need for prototyping or simulating as part of the elicitation
+process. In the case of the \emph{unknown knowns}, the analyst can
+elicit tacit knowledge by taking into account the background (political,
 cultural, emotional) of stakeholders, and use that background as an
 ``emotional guidance'' in order to draw out the relevant information.
-Finally, in order to deal with \emph{unknown unknowns} the authors
+Finally, in order to deal with \emph{unknown unknowns}, the authors
 suggest two main approaches. The first one is based on the
 ``over-the-horizon'' knowledge which is a socio-technical approach based
-on social media and e-communities. And the other one is using counter
-examples that can challenges the boundaries of the idea under
+on social media and e-communities. And the other one is based on counter
+examples that can challenge the boundaries of the idea under
 development.
@@
 One of the major causes of ambiguities in elicitation interviews is the
-presence of tacit knowledge. In some cases ambiguities can't be always
-be explained as separated term, sometimes it is required to have a
+presence of tacit knowledge. In some cases, ambiguities can't be
+explained as separated terms, sometimes it is required to have a
 context. Even under these circumstances, the analyst must be able to
 identify and alleviate them in order to elicit relevant information of
-the system. For this purpose it is necessary to provide the analyst with
-proper tools. In this paper Yehia Elrakaiby et al.~proposed a
+the system. For this purpose, it is necessary to provide the analyst
+with proper tools. In this paper, Yehia Elrakaiby et al.~proposed a
 theoretical framework to overcome ambiguity during interviews in the
@@
 
-In the paper, statements given by the stakeholders, analysts domain
-knowledge and analysts inferences are modeled as arguments, and
-ambiguities between them as attacks. For example, let say the analyst
-listens the following statement \emph{the professor will upload the task
-description within three days} (A1), but the analyst know (domain
+In the paper, statements given by the stakeholders, analysts' domain
+knowledge and analysts' inferences are modeled as arguments, and
+ambiguities between them as attacks. For example, let's say the analyst
+listens to the following statement: \emph{the professor will upload the
+task description within three days} (A1), but the analyst knows (domain
 knowledge) that \emph{the professor may be on a business meeting} (A2),
-so the analyst think (inference) that \emph{it may be possible that it
+so the analyst thinks (inference) that \emph{it may be possible that it
 will be take longer to upload the task description} (A3). In this
@@
 
-In this paper Aranda et al.~studied the influence of the analyst domain
+In this paper, Aranda et al.~studied the influence of the analyst domain
 knowledge on the effectiveness of elicitation interviews. The main
@@
 the influence of the training in requirements engineering in elicitation
-interviews. In the study participated post-graduated students as
-interviewers and two professors as interviewees. The students should
-make open interviews and elicit the information afterwards. Moreover,
-for each domain problem the students were separated in two groups based
-on their level of domain knowledge, \emph{domain-aware} and
+interviews. In the study, post-graduated students participated as
+interviewers and two professors as interviewees. The students had make
+open interviews and elicit the information afterwards. Moreover, for
+each domain problem the students were separated in two groups based on
+their level of domain knowledge, \emph{domain-aware} and
 \emph{domain-ignorant}. On the other hand, the effectiveness of the
-elicitation's was based on the comparison between the number of
-concepts, processes and requirements elicited by the students and the
-benchmarks.
+elicitation was based on the comparison between the number of concepts,
+processes and requirements elicited by the students and the benchmarks.
 
@@
 domain knowledge of the interviewees has statistically significant
-influence. Supplementary, the results of the internal replication also
+influence. Supplementarily, the results of the internal replication also
 suggest that the domain knowledge of the stakeholders is more relevant
 than the analysts', in terms of effectiveness of elicitation interviews.
-Nevertheless, these results also show that the positive effects of the
+Nevertheless, these results also show the positive effects of the
 training in requirements engineering of the interviewers, with these
@@
 
-Many analyst consider interviews the most important elicitation
-technique, and usually elicitation process starts with interviewing the
-stakeholders. Interviews allow analysts to check their understanding
+Many analysts consider interviews the most important elicitation
+technique, and usually the elicitation process starts with interviewing
+the stakeholders. Interviews allow analysts to check their understanding
 about the problem domain immediately and ask for clarifications.
-Moreover, this technique is versatile in the sense of it is possible
-that new and unexpected issues come up and they can be attacked at that
-moment.
+Moreover, this technique is versatile in the sense of being possible
+that new and unexpected issues come up and be attacked at that moment.
 
-However, elicit tacit knowledge in interviews is still a hard task to
-do. This tacit knowledge can be classified in four groups as describe in
-{[}6{]}. The \textbf{known knowns}, \textbf{known unknowns},
-\textbf{unknown knowns} and \textbf{unknown unknowns}. The known knowns
-is the knowledge that is documented, expressible, and relevant to the
-system. In order words, is the scenario in which it is possible to
-elicit since the beginning all the requirements, there is no tacit
-knowledge. The known unknowns is the knowledge that cannot be
-expressible because the stakeholders are not aware of their lack of
-domain knowledge, their might forget it. In this case analyst are aware
+However, eliciting tacit knowledge in interviews is still a hard task to
+do. This tacit knowledge can be classified in four groups as described
+in {[}6{]}. The \textbf{known knowns}, \textbf{known unknowns},
+\textbf{unknown knowns} and \textbf{unknown unknowns}. The \emph{known
+knowns} is the knowledge that is documented, expressible, and relevant
+to the system. In other words, it is the scenario in which it is
+possible to elicit from the beginning all the requirements, there is no
+tacit knowledge. The \emph{known unknowns} is the knowledge that cannot
+be expressible because the stakeholders are not aware of their lack of
+domain knowledge, they might forget it. In this case, analyst are aware
 of the domain knowledge and therefore, their job is to challenge
 assumptions or implications in order to elicit information that
-stakeholders are unaware of. The unknown knowns is the knowledge that
-stakeholders hold but it is not documented by some reason. Thus,
+stakeholders are unaware of. The \emph{unknown knowns} is the knowledge
+that stakeholders hold but it is not documented by some reason. Thus,
 analysts should use their interviewing skill to elicit when they spot
-any glimpse of that knowledge. The unknown unknowns is the knowledge
-that neither the analysts nor stakeholders are aware but might be
-relevant to the project.
+any glimpse of that knowledge. The \emph{unknown unknowns} is the
+knowledge that neither the analysts nor stakeholders are aware of, but
+might be relevant to the project.
 
@@
 
-The unknowness clarification presented in above suggest the presence of
+The unknowness clarification presented in above suggests the presence of
 three problems. The goal is to go from any scenario in which tacit
 knowledge exists to known knowns. In order to achieve that goal and take
-the advantages presented in elicitation interviews (immediately
+the advantages presented in elicitation interviews (immediate
 clarification of assumptions and debate of implications) we are going to
@@
 framework we model the interview as a set of arguments and attacks
-between them. In that sense, we will able to spot ambiguities and tacit
-knowledge in terms of inconsistencies and insufficiency of information.
-We will adapt some examples from {[}3{]} to show how each tacit
-knowledge scenario can be addresed.
+between them. In that sense, we will be able to spot ambiguities and
+tacit knowledge in terms of inconsistencies and insufficiency of
+information. We will adapt some examples from {[}3{]} to show how each
+tacit knowledge scenario can be addresed.
 
-\textbf{known unknowns}: In the following example the domain knowledge
+\textbf{known unknowns}: In the following example, the domain knowledge
 of the analyst is used to detect inconsistencies (attacks), because the
@@
 
-A customers wanted a recycling-support system and one of the goals was
+A customer wanted a recycling-support system and one of the goals was
 \emph{to avoid fines from the municipality for incorrect recycling}.
@@
 
-\textbf{unknown knowns}: In the following example analyst challenges the
-stakeholder statement, as a result the stakeholder reveals new
+\textbf{unknown knowns}: In the following example, analyst challenges
+the stakeholder's statement, as a result, the stakeholder reveals new
 information (reply).
 
-A customers wants to develop a system to allow patients to measure the
+A customer wants to develop a system to allow patients to measure the
 amount of glucose in their blood, and then send the result to their
@@
 \emph{in one-two days the doctor sees the notification in the system}.
-Then analyst asked: \emph{What happens if the doctor is not available
-for any reason?}. The customer replied: \emph{The general practitioner
-is substituted by another doctor who accesses the same system}.
+Then the analyst asked: \emph{What happens if the doctor is not
+available for any reason?}. The customer replied: \emph{The general
+practitioner is substituted by another doctor who accesses the same
+system}.
 
@@
 did and asked for clarification. However, the stakeholder couldn't give
-an answers due to his ignorance.
+an answer due to his ignorance.
 
@@
 In the last section we present how to use a theoretical framework based
-on arguments and attacks to addressed the different levels of tacit
+on arguments and attacks to be addressed the different levels of tacit
 knowledge. In this section we will compare in which scenario of tacit
@@
 
-The works presented in {[}4{]} concludes that: (1)analyst's domain
+The work presented in {[}4{]} concludes that: (1)analyst's domain
 knowledge(ADK) has small but statistically significant effect on the
@@
 general training in requirement activities have also a big positive and
-significant influence. In this paper, we will focus only in comparing
-based on the domain knowledge holder since that knowledge can be
-measured.
+significant influence. In this paper, we will focus only in the
+comparison between scenarios of tacit knowledge based on the domain
+knowledge holder since that knowledge can be measured.
 
@@
 
-We can observed in Table 1 that it is more likely to be effective in the
+We can observe in Table 1 that it is more likely to be effective in the
 scenario of \emph{unknown knowns} because the stakeholders' domain
-knowledge have more influence than analyst's domain knowledge. On the
+knowledge has more influence than analyst's domain knowledge. On the
 other hand, the analyst's interviewing skills will have different
@@
 
-Elicitation interviews is not an easy task. Like in any intensive oral
-communication there are misunderstandings related to tacit knowledge. In
-our work we focus on analyzing the different levels of how tacit
+Elicitation interviews are not an easy task. Like in any intensive oral
+communication, there are misunderstandings related to tacit knowledge.
+In our work we focus on analyzing the different levels of how tacit
 knowledge{[}6{]} would affect the effectiveness of elicitation
@@
 {[}3{]} to identify and manage tacit knowledge during interviews. And
-finally, we analyze based on the results of {[}4{]} in which scenario of
-tacit knowledge it is more likely to have a successful elicitation
+finally, we analyze, based on the results of {[}4{]}, which scenario of
+tacit knowledge is more likely to have a successful elicitation
 interview.
